### 2014-08-04 ms.tex
Sketch of paper

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{natbib}

\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$>$}}}
\newcommand{\rs}{r_s}
\newcommand{\rb}{r_b}
\newcommand{\vw}{v_w}
\newcommand{\cs}{c_s}

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}
\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}
\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\Mstar}{M_{*}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\ff}{\rm ff}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\sigsoi}{\sigma_{\soi}}
\newcommand{\vwO}{v_{w,0}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\pyear}{{\rm yr}^{-1}}

\topmargin -1 cm
\defcitealias{WangMerritt:2004a}{WM04}

\author[Generozov, Metzger, \& Stone]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger$\footnotemark[1]$\\
Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

\begin{document}
\title{Constraining Supermassive Black Hole Environments.}
 \maketitle

\begin{abstract}
Abstract here 
\end{abstract}

 \begin{keywords}
 black hole physics --  galaxies: active
 \end{keywords}

\section{Introduction}
\label{sec:introduction}

%%Maybe active galaxies constitute 10% need reference here?
Supermassive black holes (SMBHs) are present in the centers of most,
if not all nearby galaxies (see reviews by, e.g. \citealt{KormendyRichstone:1995a};
\citealt{FerrareseFord:2005a}). Roughly $\sim 1\%$ of these manifest themselves as luminous Active Galactic Nuclei. However, quiescent black holes constitute a silent majority.

In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.  The accretion rate in turn has implications for rate of black hole growth.

The gas environment also plays an important role in determining observables (light-curves, SEDs) from jetted tidal disruption events (TDEs). These are bright flares that occur when a star passes within the tidal disruption radius of the SMBH. A small fraction of such events are accompanied by the launch of a relativistic jet into the circumnuclear medium (CNM) of the host galaxy.  As the jet propagates into the CNM, a reverse shock propagates towards the back of the jet, decelerating it. The CNM density profile will determine the final Lorentz factor of the jet. This in turn will strongly affect the duration of the observed synchotron radiation.

The gas in the vicinity of a black hole may come from several sources. \citealt{Ho:2009a} proposes three different mechanisms (1) Mass loss in winds (particularly from evolved stars) (2) Stellar-stellar collisions in dense environments (3) Tidal disruptions of stars. To estimate (a lower limit on the accretion rate), \citealt{Ho:2009a} calculates the Bondi accretion rate based on typical observed gas densities and temperatures taken from Chandra X-ray observations. A second estimate is obtained from the wind mass loss rate from the observed stellar densities. Both of the estimates suggest that there is an ample reservoir of gas to power active galactic nuclei in quiescent galaxies. This suggests that the lack of the AGN activity is due to the fact that the the accretion proceeds in a radiatively inefficient mode.

Previous studies used Chandra observations to show that the Bondi accretion power well-correlated with jet power \citep{AllenDunn+:2006a,Fujita+:2013a}. In these studies temperature, and density information are inferred from Chandra x-ray observations, while the jet power is inferred from the energy required to inflate observed bubbles within the x-ray emitting gas.

However, this approach has limitations. Due to resolution issues it is almost never possible to observationally determine the gas density at the black sphere of influence, and such studies are forced to extrapolate observed gas temperatures and densities to smaller scales.  In fact, the temperature profile is assumed to be flat inside of the Bondi radius.  In reality, the cusp in the velocity dispersion near the SMBH, should cause a cusp in the gas temperature profile (assuming the kinetic energy of stellar winds is efficiently themalized in shocks). 
%%AG-give sense of scale.

Another approach to constraining the gas density around an SMBH is to go from a stellar mass loss rate (motivated by observed stellar densities) to a steady-state gas profile. This approach was taken by \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}.

%In this study we perform hydrodynamic modeling to solve for the steady-state gas density, temperature and velocity profiles near the SMBH sphere of influence, for a sample of nearby, quiescent galaxies. We a adopt the model used by \cite{Quataert:2004a} for the galactic center: gas is supplied by stellar winds, which collide, shock heat, and thermalize.  
We take the same approach. To the best of our knowledge a systematic study of the parameter space of central galaxy properties. Thus, we compute central density profiles for a broad sample of galaxies for \cite{WangMerritt:2004a}--henceforward \citetalias{WangMerritt:2004a}.  This allows us to determine to relate the central stellar properties (e.g. stellar density slope) to the central gas properties.

We also explore the effects of varying the heating rate on the flow structure. Typically an inflow outflow flow structure is established. The stellar ejecta inside of the stagnation radius ($\rs$) will be accreted, while that outside $\rs$ will be driven out with the outflow. The location of $\rs$ and hence the accretion rate is  quite sensitive to the assumed heating rate.  In fact, as the specific thermal energy of the ejects drops below the potential, an inflow is established out to the radius where the SNe Ia rate becomes comparable to the dynamical timescale, which for black holes smaller than 10$^8 \Msun$ is well outside the $\rsoi$ 
%It turns out that in our models the mass accretion rate is coincidentally quite similar to the Bondi accretion rate.

 %%AG--say something about x-ray observations.

\section{Sample}
Describe WM/Nuker sample here.

\section{Model}
We use the same model as \citealt{Quataert:2004a} to find a steady state gas density near the SMBH for each of the galaxies within our sample.  Gas is supplied by winds from the stellar population in the galactic center. Assuming a rate of mass injection, $q$, spherical symmetry and an ideal gas equation of state.

\begin{align}
&\drhodt+\frac{1}{r^2}\dxdy{\rho r^2 v}{r}=q\\
&\rho \frac{dv}{dt}=-\dpdr-\rho \dphidr-q v\\
&\rho T \frac{ds}{dt}=q\left[\ke+\kew+\gammaf \cs \right]
\end{align}

These or similar equations have been solve many times in the literature (e.g. \citealt{HolzerAxelford1971a,Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}). \citealt{ShcherbakovWong+:2014a} solves similar equation, with additional terms to account for thermal conduction and radiative cooling. However, we find that radiative cooling may be neglected for a large portion of our parameter space--\S~\ref{sec:cooling}.  Additionally thermal conduction may be cut off by magnetic field lines--\S~\ref{sec:conduction}

$q$ represent the rate of injection of gas mass per unit volume, and is derived from the stellar density, $\rho_*$, using

\begin{align}
q=\frac{\eta \rho_*}{t_h}
\end{align}

%%AG $eta/th$ is the specific of rate of mass return to the ISM.  Ciotti et al. 1991 -- see in particular Table 2. 
Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this 
number will lie in the range $\sim$0.1-1. We adopt $\eta=1$. However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.

$v_w^2/2$ encapsulates heating in our simulation. We take $v_w^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.

\section{Solutions}
\subsection{Analytics: Location of Stagnation Radius}
It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density at $\rs$.

Consider the steady-state entropy equation.

\begin{align}
&\rho T v \dsdr=\Q\\
&\dsdr=\frac{\Q}{\rho T v} \label{eq:ss_entropy}
\end{align}

At $\rs$, the velocity, $v$ goes to zero.  Therefore, the numerator must also go to 0 at $\rs$. This implies

\begin{align}
 &\kew-\gammaf \cs=0\\
 &\cs=\gammafi \kew\\
 &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}
\end{align}

From the first law of thermodynamics

\begin{align}
T\dsdr&=\ddr{u}+p\ddr{(1/\rho)}\\
&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho^2}\ddr{\rho}\\
&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho} \underbrace{\dxdy{\log{\rho}}{\log{r}}}_{-n} \label{eq:first_law}
\end{align}

Combining Equation~\ref{eq:first_law} and Equation~\ref{eq:ss_entropy}, one obtains.

\begin{align}
\frac{1}{\gamma-1}\ddr{(p/\rho)}+r n \cs=\frac{\Q}{\rho  v} \label{eqn:combo1}
\end{align}

At the stagnation point we also have (from the momentum equation)

\begin{align}
&\frac{1}{\rho}\dpdr=-\dphidr\\
&\ddr{(p/\rho)}-r n \cs=-\dphidr \label{eqn:HSE}
\end{align}

Then multiplying Equation~\ref{eqn:HSE}  $\frac{1}{\gamma-1}$ and subtracting it from Equation~\ref{eqn:combo1} we obtain

\begin{align}
\gammaf r n \cs = \frac{1}{\gamma-1} \dphidr + \frac{\Q}{\rho  v}
\end{align}

From the above equation we may obtain an expression for the Stagnation point using L'Hopital's rule and Equation~\ref{eq:tstag}. To obtain an analytic expression, we take $\Mstar\sim r^{2-\Gamma}$

\begin{align}
&\kew n =A \phirs -B \frac{G \Mbh}{\rs}\\
&A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} \label{eq:stag_analytic}
\end{align}

Note that in the above expression $\Mstar$ is evaluated at the stagnation radius. Let $\omega=\Mstar(\rs)/\Mbh$ and 
$\eta=v_{w,0}/\sigma_{\rm soi}$. We may re-parameterize this relationship as follows:

\begin{align}
\x=\frac{1}{\eta^2 n}\left[ (1+\omega)\left(A-\frac{n}{2}\right)-B\right]
\end{align}

Note that in general $\omega$ is an implicit function of $x$. Cusp galaxies have $\Gamma\simeq1$.  Then $\omega=x$. With $\gamma=5/3$, $A=2$ and $B=1/4$.  Then:

\begin{align}
\x=\frac{7-2n}{2\eta^2 n+2n-8}
\end{align}

Consider the limit $\lim_{\eta \to 0}$ (the extra heating $\vwO$ goes to 0. Then we will get a negative value for the stagnation radius unless the gas density profile is quite steep at the $\rs$: $3.5<n<4$...

In contrast for a core galaxy we will have $\Gamma\simeq0, A=9/4, B=1/2$, and  $\omega=x^2$. Thus we will have a quadratic equation for stagnation radius, which gives

\begin{align}
\x=\frac{\eta^2 n \pm \sqrt{\eta^4 n^2 -4 \left(\frac{9}{4}-\frac{n}{2}\right) \left(\frac{7}{4}-\frac{n}{2}\right)}}{2\left(\frac{9}{4}-\frac{n}{2}\right)}
\end{align}

Consider the limit $\lim_{\eta \to 0}$, then for $\rs$ to exist we must have $3.5<n<4.5$.

When $\Mstar << \Mbh$ at the stagnation radius, the relationship between $\rs$ and $\vw$ is greatly simplified.

\begin{align}
\kew=\frac{7}{4}\frac{G \Mbh}{n \rs}
\label{eq:stag_simple}
\end{align}

Where the pre-factor on the right-hand side is valid for $\gamma=5/3$ and $\Gamma=1$ or 0.

\subsection{Comparison with Bondi Accretion}
The Bondi accretion rate, $\dotMb$ is given by

\begin{align}
\dotMb=4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b)
\end{align}

where $rb=G M/\cs^2$.

%%AG: I am not entirely comfortable with this approximation for the accretion rate. 
In our model the accretion rate may be approximated as the mass enclosed with $\rs$ divided by the free-fall time.

\begin{align}
&\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}}\\
&=\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
\end{align}

Note that to within factors of order unity this is the same as Bondi formula, except $\rb$ is replaced by $\rs$. 
From Equation~\ref{eq:stag_simple}

\begin{align}
\rs=\frac{7}{2}\frac{G \Mbh}{\vw^2}.
\end{align}

Where have set $n~1$.  At $\rs$ we have

\begin{align}
\kew=\frac{c_s^2}{\gamma-1}
\end{align}

Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to the

%%AG-I still believe that one will not get an outflow without extra heating, but this statement apparently depends on the slope of the density profile...Perhaps some sort of stability arguments could be applied...perturbing density at constant pressure. What happens to the equation for HSE.
%%AG-I believe that in the case of core galaxy, the negative root of the quadratic should be taken...

\subsection{Numerics: Full numerical solution for galaxy sample}
We compute solution for our sample of galaxies for three different values of $v_{w,0}$: 1000 km/s, 500 km/s, and 200 km/s.

We show show three representative profiles in Figure~\ref{fig:profiles} below.

We show the numerical results for $\x$ vs. $\eta$ in the top panel of Figure~\ref{fig:stag}.  The three different colors represent the three different chosen values of $\vwO$. The square points represent cusp galaxies, whereas the triangles represent core galaxies.  The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.

Using the slope of the density profile, at the stagnation radius we may use Equation~\ref{eq:stag_analytic} to compute $\x$ analytically. We plot the fractional difference between the numerical and analytic results for $\x$ for each galaxy in the bottom panel of Figure~\ref{fig:stag}.  Generally, the agreement is quite good (especially for $\vwO$=1000 km/s and $\vwO$=500 km/s), providing a useful check of the numerical results.

%%AG: Describe conservation checks to additionally validate the results.

\begin{figure}
\includegraphics[width=\columnwidth]{profiles.eps}
\caption{\label{fig:profiles}Radial for three different galaxies: NGC1172, NGC4478, and NGC3115. Solid curves correspond to $v_w$=1000 km/s.
The Dot-dashed curve corresponds to $v_w$=200 km/s. Top panel: Density; 
Middle Panel: Temperature; Bottom Panel: X-ray luminosity enclosed within radius $r$.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{rs.eps}
\caption{\label{fig:stag}$\x$ vs. $\vwNorm$}
\end{figure}

\section{Discussion}
\subsection{Heating}
We now discuss potential sources of heating and discuss how different physical sources of heating would lead to different values of $\vwO$. For each heating source  from the specific heating rate $E$ we may estimate the corresponding $\vwO$...

\begin{enumerate}
\item \emph{Stellar winds} The contribution to the heating rate from the red giant winds themselves will be negligible, as red giants have wind velocities $\lsim 40$ km/s.

Although red giant winds dominate the mass budget, winds from main sequence stars may make a significant contribution to the energy budget, with wind velocities $\sim 100-150$ km/s \citep{NaimanSoares-Furtado+:2013a}. 
%%Even assuming efficient thermalization wouldn't the contribution of main sequence winds be diluted by the fraction they take up of the mass budget.

\item \emph{Type Ia SNe} Following \citealt{ShcherbakovWong+:2014a}, the energy injected per Ia SNe is 10$^{51}$ ergs, and the SNe rate is $\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$.  Assuming that each SNe in 10$^{51}$ ergs and a mass injection rate (from stellar winds) of 10$^{-11} \Msun$  yr$^{-1}$, this leads to $\vwO\simeq 600$ km/s.  (Note one of our chosen values for $\vwO$ is 500 km/s).

As noted in \citealt{ShcherbakovWong+:2014a}, it is not obvious whether or not the SNe energy injection treated as a constant throughout time and space, since the flow time-scale may be short compared to the time between successive SNe Ia...
%Thornton and Benton...
\item \emph{MS Pulsars} 
\end{enumerate}

\subsection{Mass accretion rate}
For each of our solutions, we may calculate the accretion rate $\dot{M}$ onto the SMBH. We show $\Medd$ vs. $\Mbh$ as a function of black hole mass for our three  chosen values of the $\vwO$ (200 km/s, 500 km/s, and 1000 km/s). The results are shown in Figure~\ref{fig:mdot_mass}

We find there is a trend of $\eddr$ increasing towards higher black hole masses. However, previous work  suggests a downsizing trend: for quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{Miller+:2013a}. If $L_X\sim\dot{M}^2$, this would suggest $\eddr\sim \Mbh^{-0.6}$. In contrast for fixed $\vwO$ and $\eta$ we obtain that $\eddr\sim \Mbh^{0.5-1}$. One possible solution is that $\eta$ decreases with $\Mbh$. $\dot{M}$ scales linearly with $\eta$, so we would need to have $\eta\sim \Mbh^{-1}$ to explain the observed downsizing trend.

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_mass.eps}
\caption{\label{fig:mdot_mass}$\eddr$ vs. $\Mbh$}
\end{figure}

%%AG: Split galaxies into cores (squares) and cusps (triangles). For cores only did those galaxies which had all three values of the wind velocity completed. Also want to include a plot of x-ray luminosity (less abstract than the mass accretion rate).

\subsection{Comparison with observations}
\citealt{AllenDunn+:2006a} use Chandra x-ray observations to infer the temperature and density profiles for nine nearby x-ray luminous elliptical galaxies.  Five of the galaxies in their sample overlap with that in \citetalias{WangMerritt:2004a}.

We may compare our results for the $T$ and $\rho$ profiles of the overlapping galaxies, with those inferred from observations.  Note that we we have two free parameters ($\eta$ and $\vwO$ in our model and thus we can can always match $T$ and $\rho$ at least one point.  We generally find that $\vwO=500$ km/s (as would be expected from SNe Ia) gives rough agreement with the observed temperatures.  Thus, we choose $\vwO=500$ km/s.  We choose an $\eta$ so that our solution would be consistent with the observed density profiles. The comparison is shown in Figure~\ref{fig:allen_compare}.

\begin{itemize}
\item \emph{NGC4486} On scales of $\sim1$ kpc the density profile in \citealt{AllenDunn+:2006a}  is shallower than in our model. Our model has a break in the gas density at $\sim 300$ pc--near the location of the Nuker break radius for this galaxy at 560 pc. There is an observed break in the density, but on a scale of a few kpc.

In contrast to a naive extrapolation of the observed $T$ and $\rho$ to smaller scales, our models have $T$ and $\rho$ monotonically increasing towards the galactic center. The increase in $T$ is due to the increased velocity dispersion (and thus increased heating) towards the galactic center.
\end{itemize}

\begin{figure*}
\includegraphics[width=\columnwidth]{T_compare.eps}
\includegraphics[width=\columnwidth]{dens_compare.eps}
\caption{\label{fig:allen_compare} Comparison to \citealt{AllenDunn+:2006a}}
\end{figure*}

\subsection{Cooling}
\label{sec:cooling}

\subsection{Conduction}
\label{sec:conduction}{

\subsection{Angular Momentum}

\section{Summary}

\footnotesize{
  \bibliographystyle{mn2e}
  \bibliography{master}
}
\end{document}

### 2014-08-04 ms.tex
Fixing some typos

@@
 \newcommand{\vw}{v_w}
-\newcommand{\cs}{c_s}
 
@@
 
-\author[Generozov, Metzger, \& Stone]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger$\footnotemark[1]$\\
+\author[Generozov, Metzger, \& Stone]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Brian~D.~Metzger, Nicholas Stone$\footnotemark[1]$\\
 Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
@@
 
-Previous studies used Chandra observations to show that the Bondi accretion power well-correlated with jet power \citep{AllenDunn+:2006a,Fujita+:2013a}.
+Previous studies used Chandra observations to show that the Bondi accretion power well-correlated with jet power \citep{AllenDunn+:2006a,FujitaKawakatu+:2014a}.
 In these studies temperature, and density information are inferred from Chandra x-ray observations, while the jet power is inferred from the energy required to inflate observed bubbles within the x-ray emitting gas.
@@
 To the best of our knowledge a systematic study of the parameter space of central galaxy properties.
-Thus, we compute central density profiles for a broad sample of galaxies for \cite{WangMerritt:2004a}--henceforward \citetalias{WangMerritt:2004a}.
-This allows us to determine to relate the central stellar properties (e.g.
-stellar density slope) to the central gas properties.
+Thus, we compute central density profiles for a broad sample of galaxies from \citealt{WangMerritt:2004a}--henceforward \citetalias{WangMerritt:2004a}.
+This allows us to relate the central stellar properties (e.g.
+the slope of the stellar density) to the central gas properties.
 
@@
 These or similar equations have been solve many times in the literature (e.g.
-\citealt{HolzerAxelford1971a,Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-\citealt{ShcherbakovWong+:2014a} solves similar equation, with additional terms to account for thermal conduction and radiative cooling.
+\citealt{HolzerAxford:1970a,Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
+\citealt{ShcherbakovWong+:2014a} adds additional terms to account for thermal conduction and radiative cooling.
 However, we find that radiative cooling may be neglected for a large portion of our parameter space--\S~\ref{sec:cooling}.
@@
 \begin{align}
-\dotMb=4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b)
+\Mdotb=4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b)
 \end{align}
 
-where $rb=G M/\cs^2$.
+where $r_b=G M/c_s^2$.
 
@@
 
-Where have set $n~1$.  At $\rs$ we have
+Where have set $n=1$.  At $\rs$ we have
 
@@
 
-Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to the
+Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to \Mdotb
 
@@
 As noted in \citealt{ShcherbakovWong+:2014a}, it is not obvious whether or not the SNe energy injection treated as a constant throughout time and space, since the flow time-scale may be short compared to the time between successive SNe Ia...
-%Thornton and Benton...
+%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
+%AG-Case of no stagnation radius
 \item \emph{MS Pulsars} 
@@
 $\Mbh$ as a function of black hole mass for our three  chosen values of the $\vwO$ (200 km/s, 500 km/s, and 1000 km/s).
-The results are shown in Figure~\ref{fig:mdot_mass}
+The results are shown in Figure~\ref{fig:mdot_mass}.
+%%AG-Also want to go into the case of no stagnation radius
 
 We find there is a trend of $\eddr$ increasing towards higher black hole masses.
-However, previous work  suggests a downsizing trend: for quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{Miller+:2013a}.
+However, previous work  suggests a downsizing trend: for quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.
 If $L_X\sim\dot{M}^2$, this would suggest $\eddr\sim \Mbh^{-0.6}$.
@@
 
-We may compare our results for the $T$ and $\rho$ profiles of the overlapping galaxies, with those inferred from observations.
+We may compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.
 Note that we we have two free parameters ($\eta$ and $\vwO$ in our model and thus we can can always match $T$ and $\rho$ at least one point.
@@
 The comparison is shown in Figure~\ref{fig:allen_compare}.
+%%AG-The chosen properties, in particular eta may be summarized in a table.
 
 \begin{itemize}
-\item \emph{NGC4486} On scales of $\sim1$ kpc the density profile in \citealt{AllenDunn+:2006a}  is shallower than in our model.
+\item \emph{NGC4486} %eta=0.2
+On scales of $\sim1$ kpc the density profile in \citealt{AllenDunn+:2006a}  is shallower than in our model.
 Our model has a break in the gas density at $\sim 300$ pc--near the location of the Nuker break radius for this galaxy at 560 pc.
@@
 \includegraphics[width=\columnwidth]{dens_compare.eps}
-\caption{\label{fig:allen_compare} Comparison to \citealt{AllenDunn+:2006a}}
+\caption{\label{fig:allen_compare} Comparison of $n_e$ and $T$ to the \citealt{AllenDunn+:2006a}}. 
+%%AG in the future we will have to be carfeful of the mean molecular weight.
 \end{figure*}

### 2014-08-04 ms.tex
Some comments on Mdot.

@@
 \subsection{Comparison with Bondi Accretion}
-The Bondi accretion rate, $\dotMb$ is given by
+The Bondi accretion rate, $\Mdotb$ is given by
 
@@
 
-Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to \Mdotb
+Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to $\Mdotb$
 
@@
 The results are shown in Figure~\ref{fig:mdot_mass}.
+Note that $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy.
+Thus, the mass accretion rate will be a sensitive function of the assumed heating rate.
+%%AG-Core galaxies might be a better choice to show the variations in the mass accretion rate 
 %%AG-Also want to go into the case of no stagnation radius

### 2014-08-11 ms.tex
Typo
Rewrite of heating section and cooling

@@
 \newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
+\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
 \newcommand{\Mdotb}{\dot{M}_{\rm bondi}}
@@
 \newcommand{\Menc}{M_{\rm enc}}
-\newcommand{\Mstar}{M_{*}}
+\newcommand{\rhostar}{\rho_*}
+\newcommand{\Mstar}{M_{\star}}
 \newcommand{\Mbh}[1][]{M_{\bullet#1}}
@@
 \newcommand{\rsoi}{r_{\soi}}
+\newcommand{\rIa}{r_{\rm Ia}}
 \newcommand{\sigsoi}{\sigma_{\soi}}
@@
 \begin{document}
-\title{Constraining Supermassive Black Hole Environments.}
+\title{Constraining Quiescent Supermassive Black Hole Environments.}
  \maketitle
@@
 These are bright flares that occur when a star passes within the tidal disruption radius of the SMBH.
-A small fraction of such events are accompanied by the launch of a relativistic jet into the circumnuclear medium (CNM) of the host galaxy.
+A small fraction of   events are accompanied by the launch of a relativistic jet into the circumnuclear medium (CNM) of the host galaxy.
 As the jet propagates into the CNM, a reverse shock propagates towards the back of the jet, decelerating it.
@@
 The location of $\rs$ and hence the accretion rate is  quite sensitive to the assumed heating rate.
-In fact, as the specific thermal energy of the ejects drops below the potential, an inflow is established out to the radius where the SNe Ia rate becomes comparable to the dynamical timescale, which for black holes smaller than 10$^8 \Msun$ is well outside the $\rsoi$
+%In fact, as the specific thermal energy of the ejects drops below the potential, an inflow is established out to the radius where the SNe Ia rate becomes comparable to the dynamical timescale, which for black holes smaller than 10$^8 \Msun$ is well outside the $\rsoi$
 %It turns out that in our models the mass accretion rate is coincidentally quite similar to the Bondi accretion rate.
@@
 \rs=\frac{7}{2}\frac{G \Mbh}{\vw^2}.
+\label{eq:rs_simple}
 \end{align}
@@
 
-%%AG-I still believe that one will not get an outflow without extra heating, but this statement apparently depends on the slope of the density profile...Perhaps some sort of stability arguments could be applied...perturbing density at constant pressure.
-What happens to the equation for HSE.
+%%AG-Apparently even in the low heating case, it is still possible to an outflow (from the analytic results above the gas density must be quite steep in this case).
+However, at low heating we will probably become subject to a cooling instablity.
 %%AG-I believe that in the case of core galaxy, the negative root of the quadratic should be taken...
@@
 We now discuss potential sources of heating and discuss how different physical sources of heating would lead to different values of $\vwO$.
-For each heating source  from the specific heating rate $E$ we may estimate the corresponding $\vwO$...
+For each heating source  from the heating rate per unit volume $e$ we may estimate the corresponding $\vwO$, using
+
+\begin{align}
+&\frac{q \vwO^2}{2}=e\\
+&\frac{\eta \rhostar \vwO^2}{2 t_h}=e
+\label{eq:vw_eff}
+\end{align}
+
+We estimate the value of the $\vwO$ for different physical heating sources below.
 
@@
 Although red giant winds dominate the mass budget, winds from main sequence stars may make a significant contribution to the energy budget, with wind velocities $\sim 100-150$ km/s \citep{NaimanSoares-Furtado+:2013a}.
-%%Even assuming efficient thermalization wouldn't the contribution of main sequence winds be diluted by the fraction they take up of the mass budget.
 
-\item \emph{Type Ia SNe} Following \citealt{ShcherbakovWong+:2014a}, the energy injected per Ia SNe is 10$^{51}$ ergs, and the SNe rate is $\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$.
-Assuming that each SNe in 10$^{51}$ ergs and a mass injection rate (from stellar winds) of 10$^{-11} \Msun$  yr$^{-1}$, this leads to $\vwO\simeq 600$ km/s.
-(Note one of our chosen values for $\vwO$ is 500 km/s).
+\item \emph{Type Ia SNe} Following \citealt{ShcherbakovWong+:2014a}, the energy injected per Ia SNe is $E_{\rm Ia}=10^{51}$ ergs, and the SNe rate is $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$.
 
-As noted in \citealt{ShcherbakovWong+:2014a}, it is not obvious whether or not the SNe energy injection treated as a constant throughout time and space, since the flow time-scale may be short compared to the time between successive SNe Ia...
+\begin{align}
+e=R_{\rm Ia} E_{\rm Ia} \rhostar
+\end{align}
+
+Then from Equation~\ref{eq:vw_eff}
+
+\begin{align}
+\vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}}
+\end{align}
+
+ Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which gives $eta\simeq 230 \eta^{-1/2}$ km/s (For $\eta=0.1$ this corresponds to $\vwO\simeq$ 500 km/s.
+ %Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.
+
+As noted in \citealt{ShcherbakovWong+:2014a}, SNe energy injection cannot necessarily be treated as constant throughout  time and space, since the flow time-scale may be short compared to the time between successive SNe Ia.
+
+There will be some radius, $r_{\rm Ia}$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.
+If the stagnation radius of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$
+
+The timescale between successive Type Ia SNes  is
+
+\begin{align}
+t_{\rm Ia} \sim 2.5 \times 10^5  \Mstar_{,8}^{-1} \; {\rm yrs}.
+\end{align}
+
+The dynamical time is given
+
+\begin{align}
+ t_{\rm dyn} \sim r/\sigma \sim G M_\star/\sigma^3 \sim 5 \times 10^4 \Mstar_{,8} \sigma_{200}^{-3} \; {\rm yrs}.
+\end{align}
+
+Therefore,
+
+\begin{align}
+ r_{\rm Ia} \sim G \Mstar_{\rm Ia}/\sigma^2 \sim 4 \sigma_{200}^{-1/2} \; {\rm pc}
+\end{align}
+
 %AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
-%AG-Case of no stagnation radius
+
 \item \emph{MS Pulsars} 
+The spin down power of millisecond pulsars (MSPs) could potentially be an important heating source. Assuming a spin-down luminosity $L_{\rm sd}$ and $n_{\rm msp}$ MSPs per unit mass
+
+\begin{align}
+e=L_{\rm sd} n_{\rm msp} \rhostar.
+\end{align}
+
+Then we may obtain the $\vwO$ from Equation~\ref{eq:vw_eff}. m
+
+\begin{align}
+\vwO=\sqrt{\frac{2 t_h n_{\rm msp} L_{\rm sd}}{\eta}}
+\end{align}
+
+There may be as many 30,000 MSPs in the Milky way, which would give  $n_{\rm msp}\simeq3 \times 10^{-41} $ MSPs g$^{-1}$.
+Even if we optimistically take $L_{\rm sd}\simeq 10^{35}$ ergs/s, and $\eta$=0.1, we would get $\vwO\simeq40$ km/s, which means heating by MSPs is negligible.
+
+Note MSPs may also be dissociated in the galactic center...
+%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
 \end{enumerate}
@@
 For each of our solutions, we may calculate the accretion rate $\dot{M}$ onto the SMBH.
-We show $\Medd$ vs.
+We show $\Mdote$ vs.
 $\Mbh$ as a function of black hole mass for our three  chosen values of the $\vwO$ (200 km/s, 500 km/s, and 1000 km/s).
@@
 Thus, the mass accretion rate will be a sensitive function of the assumed heating rate.
-%%AG-Core galaxies might be a better choice to show the variations in the mass accretion rate 
-%%AG-Also want to go into the case of no stagnation radius
+%%AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
+%%AG-Note separation of cores and cusps (at vw=1000 km/s, where there are enough core galaxies for this comparison to be made). Also, note that the spread in core galaxies is far larger.
+
+The accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$, while for cusp galaxies $dot{M}\sim \Mbh (\rs/\rsoi)$.
+This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag})Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.
+For $\vwO=1000$ km/s, core galaxies have a smaller accretion rate for a given black hole mass.
 
@@
 
-%%AG: Split galaxies into cores (squares) and cusps (triangles).
-For cores only did those galaxies which had all three values of the wind velocity completed.
-Also want to include a plot of x-ray luminosity (less abstract than the mass accretion rate).
+%%AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).
 
@@
 \label{sec:cooling}
+In our models stellar winds collide, shock heat, and thermalize.
+The rate of energy injection (parameterized by $\vwO$) sets a characteristic temperature--see Equation~\ref{eq:tstag}.
+For a given amount of injected mass, the energy input from shock heating should be equal to the enthalpy of the gas.
+
+In principle, the gas should radiatively cool as well--either from metal line cooling for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim 2\times 10^7$ K.
+If the cooling rate is much smaller than the rate of energy injection then radiative cooling may be safely neglected.
+
+For each of our solutions we compare the radiative cooling rate, $C$ to the heating rate $H=q \vw^2/2$. If $H/C \gg  1$ then cooling may be neglected. We take
+
+\begin{align}
+c=\Lambda(T) n^2.
+\end{align}
+
+Where $n$ is the number density and $\Lambda(T)$ is the cooling function. We approximate $\Lambda(T)$ as piece-wise power law (fitted for solar metallicity--see Figure 34.1 in \cite{Draine:2011a})
+%cite Draine
+
+\[
+\Lambda(T)\simeq
+\begin{cases}
+    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
+    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}}& \text{if } T \lsim 2 \times 10^7 \text{K}     
+\end{cases}
+\label{eq:cooling}
+\]
+
+Note $C\propto n^2\propto \eta^2$.
+On the other hand, $H \propto q  \propto \eta$.
+Thus, the ratio $H/C$ will depend upon the free parameter $\eta$.
+We plot $H/C$ for all of our profiles for our fiducial $\eta=1$.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{cooling.eps}
+\caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate ($C$) for each of our solutions.
+The cooling rate is calculated using the approximate (solar metallicity) cooling function in Equation~\ref{eq:cooling}.
+The heating rate is estimated as $q \vw^2/2$.
+The ratio is computed assuming $eta=1$.}
+\end{figure}
+
+For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that radiative cooling may be safely neglected.
+With a few exceptions this is also true for $\vwO$=500 km/s.
+However, for $\vwO$=200 km/s cooling may be quite important.
+However, at smaller $\eta$ the effects of cooling will be less pronounced.
+For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .
+Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
+$\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.
 

### 2014-08-11 ms.tex
New figure and table

@@
 
-\item \emph{Type Ia SNe} Following \citealt{ShcherbakovWong+:2014a}, the energy injected per Ia SNe is $E_{\rm Ia}=10^{51}$ ergs, and the SNe rate is $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$.
+\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}d}$ ergs, and the SNe rate,  $R_{\rm Ia}
 
@@
 
- Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which gives $eta\simeq 230 \eta^{-1/2}$ km/s (For $\eta=0.1$ this corresponds to $\vwO\simeq$ 500 km/s.
+ Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which gives $\vwO\simeq 230 \, \eta^{-1/2}$ km/s (For $\eta=0.1$ this corresponds to $\vwO\simeq$ 500 km/s.
  %Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.
@@
 There will be some radius, $r_{\rm Ia}$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.
-If the stagnation radius of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$
+If the stagnation radius ($\rs$) of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$
 
@@
 
+...
+
+%%AG-Plot comparing stagnation radius and Ia radius for all profiles...I found this to be confusing/hard to explain.
 %AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
@@
 
-Note MSPs may also be dissociated in the galactic center...
+Also, MSPs may also be dissociated in the galactic center...
 %%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
@@
 
-In principle, the gas should radiatively cool as well--either from metal line cooling for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim 2\times 10^7$ K.
-If the cooling rate is much smaller than the rate of energy injection then radiative cooling may be safely neglected.
+The gas should radiatively cool as well--either from metal line cooling for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim 2\times 10^7$ K.
+However, if the cooling rate is much smaller than the rate of energy injection then radiative cooling may be safely neglected.
 
@@
 However, for $\vwO$=200 km/s cooling may be quite important.
-However, at smaller $\eta$ the effects of cooling will be less pronounced.
+For smaller $\eta$ the effects of cooling will be less pronounced.
 For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .
@@
 $\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.
+
+\input{figures/eta_tab.tex}
 

### 2014-08-11 ms.tex
Some changes to table, some minor improvements to language

@@
 
-The accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$, while for cusp galaxies $dot{M}\sim \Mbh (\rs/\rsoi)$.
-This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag})Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.
+The accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$, while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.
+This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag}).
+Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.
 For $\vwO=1000$ km/s, core galaxies have a smaller accretion rate for a given black hole mass.
@@
 However, for $\vwO$=200 km/s cooling may be quite important.
-For smaller $\eta$ the effects of cooling will be less pronounced.
+
+For small $\eta$ the effects of cooling will be less pronounced.
 For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .

### 2014-08-12 ms.tex
Schematic depiction of the effective wind velocity.

@@
 \newcommand{\vwO}{v_{w,0}}
+\newcommand{\kewO}{\frac{\vwO^2}{2}}
 \newcommand{\x}{\frac{r_s}{\rsoi}}
@@
 \begin{align}
-&\kew n =A \phirs -B \frac{G \Mbh}{\rs}\\
+&\kewO n =A \phirs -B \frac{G \Mbh}{\rs}\\
 &A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} \label{eq:stag_analytic}
@@
 \begin{align}
-\kew=\frac{7}{4}\frac{G \Mbh}{n \rs}
+\kewO=\frac{7}{4}\frac{G \Mbh}{n \rs}
 \label{eq:stag_simple}
@@
 \begin{align}
-\rs=\frac{7}{2}\frac{G \Mbh}{\vw^2}.
+\rs=\frac{7}{2}\frac{G \Mbh}{\vwO^2}.
 \label{eq:rs_simple}
@@
 
-Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to $\Mdotb$
+Thus, $\cs(\rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to $\Mdotb$
 
@@
 
+\item \emph{MS Pulsars} 
+The spin down power of millisecond pulsars (MSPs) could potentially be an important heating source. Assuming a spin-down luminosity $L_{\rm sd}$ and $n_{\rm msp}$ MSPs per unit mass
+
+\begin{align}
+e=L_{\rm sd} n_{\rm msp} \rhostar.
+\end{align}
+
+Then we may obtain the $\vwO$ from Equation~\ref{eq:vw_eff}. m
+
+\begin{align}
+\vwO=\sqrt{\frac{2 t_h n_{\rm msp} L_{\rm sd}}{\eta}}
+\end{align}
+
+There may be as many 30,000 MSPs in the Milky way, which would give  $n_{\rm msp}\simeq3 \times 10^{-41} $ MSPs g$^{-1}$.
+Even if we optimistically take $L_{\rm sd}\simeq 10^{35}$ ergs/s, and $\eta$=0.1, we would get $\vwO\simeq40$ km/s, which means heating by MSPs is negligible.
+
+Also, MSPs may also be dissociated in the galactic center...
+%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
+\end{enumerate}
+
 \item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}d}$ ergs, and the SNe rate,  $R_{\rm Ia}
@@
 
-...
+The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant.
+For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.
+Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating.
+Thus, for $\Mbh=10^6 \MSun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds.
+On the other hand, for $\Mbh \gsim 10^8 \MSun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe.
+These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
 
-%%AG-Plot comparing stagnation radius and Ia radius for all profiles...I found this to be confusing/hard to explain.
+\begin{figure}
+\includegraphics[width=\columnwidth]{vw_eff.eps}
+\caption{\label{fig:vw_eff} Top panel: $\vwO$ vs.
+$\Mbh/\Msun$ assuming $\vwO$=100 km/s (from main sequence winds) for $\rs/\rIa<1$ and $\vwO$=500 km/s (from type Ia SNes) for $\rs/\rIa>1$.
+Bottom panel: $\rs/\rIa$ vs.
+$\Mbh/\Msun$ using heating prescription above.}
+\end{figure}
+
+%AG-I am not comfortable saying type Ia SNe's don't contribute to heating for smaller mass BHs.
+If the cooling time for the SNe is long then it would be wrong to ignore the SNe contribution.
+The difference would be that the SNe heating would just be less steady.
 %AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
-
-\item \emph{MS Pulsars} 
-The spin down power of millisecond pulsars (MSPs) could potentially be an important heating source. Assuming a spin-down luminosity $L_{\rm sd}$ and $n_{\rm msp}$ MSPs per unit mass
-
-\begin{align}
-e=L_{\rm sd} n_{\rm msp} \rhostar.
-\end{align}
-
-Then we may obtain the $\vwO$ from Equation~\ref{eq:vw_eff}. m
-
-\begin{align}
-\vwO=\sqrt{\frac{2 t_h n_{\rm msp} L_{\rm sd}}{\eta}}
-\end{align}
-
-There may be as many 30,000 MSPs in the Milky way, which would give  $n_{\rm msp}\simeq3 \times 10^{-41} $ MSPs g$^{-1}$.
-Even if we optimistically take $L_{\rm sd}\simeq 10^{35}$ ergs/s, and $\eta$=0.1, we would get $\vwO\simeq40$ km/s, which means heating by MSPs is negligible.
-
-Also, MSPs may also be dissociated in the galactic center...
-%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
-\end{enumerate}
 

### 2014-08-22 ms.tex
Adding some description of sample/fixing compilation errors.

@@
 \newcommand{\Mstar}{M_{\star}}
+\newcommand{\Mseight}{M_{\star,8}}
 \newcommand{\Mbh}[1][]{M_{\bullet#1}}
@@
 \section{Sample}
-Describe WM/Nuker sample here.
+We start with a sample of 61 galaxies from \citetalias{WangMerritt:2004a}, as subset of a larger sample of galaxies from \citealt{FaberTremaine+:1997a}.
+These are nearby elliptical galaxies, observed with the Hubble WFPC2.
+
+For each galaxy in the sample we take the surface brightness parameterization given in Table 1 of  \citetalias{WangMerritt:2004a}. The parameterization is a Nuker law
+
+\begin{equation}
+I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \xi=\frac{r}{r_b}.
+\end{equation}
+
+This is a broken power law which transitions from an inner power law slope, $\gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
+
+From the surface brightness profile, we follow the same procedure as \citetalias{WangMerritt:2004a} to compute the spatial stellar density and stellar mass profile, both of which are used in our model.
+
+%%AG--some discussion of alternate parameterizations.
+My intuition is that for our purposes the parameterization should not matter.
+But some discussion of alternate possibilities could prevent Alistar Graham from yelling at us.
 
 \section{Model}
+\label{sec:model}
 We use the same model as \citealt{Quataert:2004a} to find a steady state gas density near the SMBH for each of the galaxies within our sample.
@@
 %%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
-\end{enumerate}
 
-\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}d}$ ergs, and the SNe rate,  $R_{\rm Ia}
+\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}$, and the SNe rate,  $R_{\rm Ia}$
 
@@
 
-There will be some radius, $r_{\rm Ia}$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.
+There will be some radius, $\rIa$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.
 If the stagnation radius ($\rs$) of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$
@@
 \begin{align}
-t_{\rm Ia} \sim 2.5 \times 10^5  \Mstar_{,8}^{-1} \; {\rm yrs}.
+t_{\rm Ia} \sim 2.5 \times 10^5 \Mseight^{-1} \; {\rm yrs}.
 \end{align}
@@
 \begin{align}
- t_{\rm dyn} \sim r/\sigma \sim G M_\star/\sigma^3 \sim 5 \times 10^4 \Mstar_{,8} \sigma_{200}^{-3} \; {\rm yrs}.
+ t_{\rm dyn} \sim r/\sigma \sim G \Mstar/\sigma^3 \sim 5 \times 10^4 \Mseight \sigma_{200}^{-3} \; {\rm yrs}.
 \end{align}
@@
 \begin{align}
- r_{\rm Ia} \sim G \Mstar_{\rm Ia}/\sigma^2 \sim 4 \sigma_{200}^{-1/2} \; {\rm pc}
+ r_{\rm Ia} \sim G \Mstar{}_{,\rm Ia}/\sigma^2 \sim 4 \sigma_{200}^{-1/2} \; {\rm pc}
 \end{align}
@@
 Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating.
-Thus, for $\Mbh=10^6 \MSun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds.
-On the other hand, for $\Mbh \gsim 10^8 \MSun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe.
+Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds.
+On the other hand, for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe.
 These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
+\end{enumerate}
 
@@
     2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
-    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}}& \text{if } T \lsim 2 \times 10^7 \text{K}     
+    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
 \end{cases}

### 2014-08-25 ms.tex
Additional detail about the role of the stellar mass function in the model.

@@
 We take $v_w^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.
+
+{\bf NCS: here is some added detail about the role of stellar mass functions in the model}
+
+If we assume that a stellar population forms impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any future time $t$ is given by
+\begin{equation}
+f(t) =\frac{ \int_{m_0}^{m_{\rm max}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
+\end{equation}
+where 
+\begin{equation}
+m_{\rm max}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
+\end{equation}
+For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
+\begin{equation}
+f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
+\end{equation}
+{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
+If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
+\begin{equation}
+q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm max}(t)) m_{\rm max}(t) \frac{df}{dt},
+\end{equation}
+where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm max}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
+\begin{equation}
+q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
+\end{equation}
+This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
+Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
+Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
+Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{NickPlot.eps}
+\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
+The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
+Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
+\end{figure}
+
+In Fig.
+\ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).
+We parametrize the wind velocity as
+\begin{equation}
+\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
+\end{equation}
+The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.
+We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.
+Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.
 

### 2014-08-31 ms.tex
Some reorganization

--- 2014-08-22 ms.tex
@@
 \usepackage{astro}
-\usepackage{natbib}
+%\usepackage{natbib}
 
+\newcommand{\Mdot}{\dot{M}}
 \newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
@@
 \newcommand{\dphidr}{\dxdy{\Phi}{r}}
+
 \newcommand{\ke}{\frac{v^2}{2}}
 \newcommand{\kew}{\frac{v_w^2}{2}}
+
 \newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
@@
 \newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
+
 \newcommand{\kb}{k_{\rm b}}
 \renewcommand{\mp}{m_{\rm p}}
+\newcommand{\pc}{\rm pc}
+
 \newcommand{\Menc}{M_{\rm enc}}
@@
 \newcommand{\Mbh}[1][]{M_{\bullet#1}}
+\newcommand{\MbhNorm}{\frac{\Mbh}{10^8 \Msun}}
+
 \newcommand{\phirs}{\frac{G \Menc}{\rs}}
 \newcommand{\soi}{\rm soi}
+\newcommand{\rsoi}{r_{\soi}}
 \newcommand{\ff}{\rm ff}
-\newcommand{\rsoi}{r_{\soi}}
+\newcommand{\tff}{t_{\ff}}
 \newcommand{\rIa}{r_{\rm Ia}}
 \newcommand{\sigsoi}{\sigma_{\soi}}
+
 \newcommand{\vwO}{v_{w,0}}
@@
 \newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
+\newcommand{\vwNormB}{\frac{\vwO}{500 \, {\rm km/s}}}
+\newcommand{\vwNormC}{\frac{\vwO}{500 \, {\rm km/s}}}
+
 \newcommand{\pyear}{{\rm yr}^{-1}}
+\newcommand{\tage}{t_{\rm age}}
 
@@
 The accretion rate in turn has implications for rate of black hole growth.
+%AG:Perhaps need more detail here.
+
+Constraints on the SMBH accretion rates at the low end of the SMBH mass function also have implications for the black occupation fraction.
+For example, \citealt{MillerGallo+:2014a} used an observed relation between $\Mbh$ and nuclear x-ray luminosity $L_x$ to constrain the BH occupation fraction.
+However, they extrapolate (assuming a single power law) their observed relationship below their detection threshold.
+However, it is possible that the $L_x$-$\Mbh$ relationship steepens at smaller $\Mbh$, and thus the black hole occupation fraction could be underestimated at low $\Mbh$.
+%AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
 
@@
 
-We also explore the effects of varying the heating rate on the flow structure.
-Typically an inflow outflow flow structure is established.
+For each galaxy in our chosen sample, we find a steady state gas profile.
+Typically an inflow-outflow structure is established.
 The stellar ejecta inside of the stagnation radius ($\rs$) will be accreted, while that outside $\rs$ will be driven out with the outflow.
+It is often assumed that the gas properties at the Bondi radius, $\rb$ set the accretion rate.
+However, physically it is really $\rs$ which sets the accretion rate.
+Typically this lies within a factor of a few of the $\rb$.
+This means that with perfect knowledge of the gas profile the $\Mdotb$ is typically a good approximation to the actual accretion rate $\Mdot$.
+However, using extrapolations of the observed gas temperature and density to estimate $\Mdot$ may cause systematic order of magnitude errors in the inferred  accretion rate.
+
 The location of $\rs$ and hence the accretion rate is  quite sensitive to the assumed heating rate.
-%In fact, as the specific thermal energy of the ejects drops below the potential, an inflow is established out to the radius where the SNe Ia rate becomes comparable to the dynamical timescale, which for black holes smaller than 10$^8 \Msun$ is well outside the $\rsoi$
-%It turns out that in our models the mass accretion rate is coincidentally quite similar to the Bondi accretion rate.
+Physically, the heating rate of the gas would vary from galaxy to galaxy.
+For example, SNe Ia may be a large source of energy for the gas.
+However, this will be only be the case for larger black holes for which the gas inflow time is smaller than the time between successive Ias.
+Thus, for smaller black holes, the effective gas heating rate may be considerably smaller.
+Thus, we investigate the effect of changing rate of energy injection on the gas density profiles.
 
@@
 These are nearby elliptical galaxies, observed with the Hubble WFPC2.
+
+We focus on elliptical galaxies to isolate the effect of mass loss from a relatively old stellar population, avoiding additional gas flowing in from star formation on larger scales.
 
@@
 This is a broken power law which transitions from an inner power law slope, $\gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
+The corresponding (spherically symmetric) stellar density, $\rhostar\sim r^{-1-\gamma}$ for $r \ll \rb$ and  $\rhostar\sim r^{-1-\beta}$ for $r \ll \rb$.
+$\gamma\simeq1$ for cusp galaxies, while $\gamma\simeq0$ for core galaxies.
+%AG:Is there a systematic dependence of beta on galaxy type$.
 
@@
 %%AG $eta/th$ is the specific of rate of mass return to the ISM.  Ciotti et al. 1991 -- see in particular Table 2. 
-Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this 
-number will lie in the range $\sim$0.1-1. We adopt $\eta=1$. However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.
+Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this number will lie in the range $\sim$0.1-1 (see Appendix~\ref{app:eta}).
+We adopt $\eta=1$.
+However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.
 
-$v_w^2/2$ encapsulates heating in our simulation.
-We take $v_w^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.
+$\vw^2/2$ encapsulates heating in our simulation.
+We take $\vw^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.
+
+%{\bf NCS: here is some added detail about the role of stellar mass functions in the model}
+
+% if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
+Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
+Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
+Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
+%
+%\begin{figure}
+%\includegraphics[width=\columnwidth]{NickPlot.eps}
+%\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
+The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
+Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
+%\end{figure}
+%
+%%In Fig.
+\ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).
+We parametrize the wind velocity as
+%\begin{equation}
+%\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
+%\end{equation}
+%The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.
+We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.
+Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.
 
 \section{Solutions}
-\subsection{Analytics: Location of Stagnation Radius}
-It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density at $\rs$.
+\subsection{Analytics: Flow properties and $\rs$}
+It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density (at $\rs$) $n$.
+We summarize the main results here and place the detailed derivation in Appendix~\ref{app:rs}.
 
-Consider the steady-state entropy equation.
+The temperature at the $\rs$ is given by
 
 \begin{align}
-&\rho T v \dsdr=\Q\\
-&\dsdr=\frac{\Q}{\rho T v} \label{eq:ss_entropy}
+ &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}\\
+ &T=6 \times 10^6 {\rm K} \, \mu \, \left({\frac{\vw}{500 \,{\rm km/s}}}\right)^2 
 \end{align}
 
-At $\rs$, the velocity, $v$ goes to zero.  Therefore, the numerator must also go to 0 at $\rs$. This implies
-
-\begin{align}
- &\kew-\gammaf \cs=0\\
- &\cs=\gammafi \kew\\
- &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}
-\end{align}
-
-From the first law of thermodynamics
-
-\begin{align}
-T\dsdr&=\ddr{u}+p\ddr{(1/\rho)}\\
-&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho^2}\ddr{\rho}\\
-&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho} \underbrace{\dxdy{\log{\rho}}{\log{r}}}_{-n} \label{eq:first_law}
-\end{align}
-
-Combining Equation~\ref{eq:first_law} and Equation~\ref{eq:ss_entropy}, one obtains.
-
-\begin{align}
-\frac{1}{\gamma-1}\ddr{(p/\rho)}+r n \cs=\frac{\Q}{\rho  v} \label{eqn:combo1}
-\end{align}
-
-At the stagnation point we also have (from the momentum equation)
-
-\begin{align}
-&\frac{1}{\rho}\dpdr=-\dphidr\\
-&\ddr{(p/\rho)}-r n \cs=-\dphidr \label{eqn:HSE}
-\end{align}
-
-Then multiplying Equation~\ref{eqn:HSE}  $\frac{1}{\gamma-1}$ and subtracting it from Equation~\ref{eqn:combo1} we obtain
-
-\begin{align}
-\gammaf r n \cs = \frac{1}{\gamma-1} \dphidr + \frac{\Q}{\rho  v}
-\end{align}
-
-From the above equation we may obtain an expression for the Stagnation point using L'Hopital's rule and Equation~\ref{eq:tstag}. To obtain an analytic expression, we take $\Mstar\sim r^{2-\Gamma}$
-
-\begin{align}
-&\kewO n =A \phirs -B \frac{G \Mbh}{\rs}\\
-&A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} \label{eq:stag_analytic}
-\end{align}
-
-Note that in the above expression $\Mstar$ is evaluated at the stagnation radius. Let $\omega=\Mstar(\rs)/\Mbh$ and 
-$\eta=v_{w,0}/\sigma_{\rm soi}$. We may re-parameterize this relationship as follows:
+We may also write an (implicit) analytic expression for $\rs$ itself. Let $\omega=\Mstar(\rs)/\Mbh$ and  $\eta=v_{w,0}/\sigma_{\rm soi}$.
 
@@
 \x=\frac{1}{\eta^2 n}\left[ (1+\omega)\left(A-\frac{n}{2}\right)-B\right]
+\label{eq:stag_analytic}
 \end{align}
-
-Note that in general $\omega$ is an implicit function of $x$. Cusp galaxies have $\Gamma\simeq1$.  Then $\omega=x$. With $\gamma=5/3$, $A=2$ and $B=1/4$.  Then:
-
-\begin{align}
-\x=\frac{7-2n}{2\eta^2 n+2n-8}
-\end{align}
-
-Consider the limit $\lim_{\eta \to 0}$ (the extra heating $\vwO$ goes to 0.
-Then we will get a negative value for the stagnation radius unless the gas density profile is quite steep at the $\rs$: $3.5<n<4$...
-
-In contrast for a core galaxy we will have $\Gamma\simeq0, A=9/4, B=1/2$, and  $\omega=x^2$. Thus we will have a quadratic equation for stagnation radius, which gives
-
-\begin{align}
-\x=\frac{\eta^2 n \pm \sqrt{\eta^4 n^2 -4 \left(\frac{9}{4}-\frac{n}{2}\right) \left(\frac{7}{4}-\frac{n}{2}\right)}}{2\left(\frac{9}{4}-\frac{n}{2}\right)}
-\end{align}
-
-Consider the limit $\lim_{\eta \to 0}$, then for $\rs$ to exist we must have $3.5<n<4.5$.
 
@@
 \begin{align}
-\kewO=\frac{7}{4}\frac{G \Mbh}{n \rs}
+&\rs=\frac{7}{2}\frac{G \Mbh}{n \vw^2}\\
+&\simeq 6 \, \pc \left(\MbhNorm\right) \left(\vwNormB\right)^{-2}
 \label{eq:stag_simple}
@@
 
-Where the pre-factor on the right-hand side is valid for $\gamma=5/3$ and $\Gamma=1$ or 0.
+This relationship will hold as long as $\vw > \sigma(\rsoi)$, or equivalently (from the $M-\sigma$ relationship) $\vwO > \left(\frac{\Mbh}{10^8 \Msun}\right)^{1/5} 200 {\rm \,  km/s}$.
+
+$\Mdot$ flowing towards the hole is given by
+
+\begin{align}
+\dot{M}=\frac{\eta \Menc(\rs)}{\rs}
+\end{align}
+
+In physical units this may be approximated as
+
+\[
+\dot{M}
+\begin{cases}
+   1.5 \time 10^{-3}  \left(\MbhNorm\right)^{1.9} \left(\vwNormB\right)^{-4} \Msun \, \pyear& \text{for core galaxies} \\
+   3.3 \times 10^{-3}   & \text{for cusp galaxies}      
+\end{cases}
+\label{eq:cooling}
+\]
+
+Finally, we may estimate the $\rho$ at $\rs$, using
+
+\begin{equation}
+\rho(\rs)\simeq q(\rs) \tff
+\end{equation}
 
@@
 \begin{align}
-\vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}}
+\vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}
 \end{align}
@@
 For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.
-Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating.
-Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds.
+Above $\sim10^8 \Msun$ SNes will represent an important contribution to the overall heating.
+%Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds.
 On the other hand, for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe.
 These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
-\end{enumerate}
+%\end{enumerate}
+
+\item \emph{Overall Heating Rate}
+The overall value of $\vwO$ has contributions from Type Ia SNes  and main sequence winds.  The relative
+contributions will depend on both the age of the stellar population, $t_{\rm age}$ and $\Mbh$.  This is
+illustrated in Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe Ia will not contribute to 
+$\vwO$ as the flow time scale is short compared to $t_{\rm Ia}$, and the heating is dominated by main
+sequence winds (with $\vwO\simeq 100$ km/s).  On the other hand, for $\Mbh \gsim 10^8 \Msun$, heating
+from Ias becomes important, as $\rs>\rIa$.  In this regime, we add the $\vwO$ values from SNe Ias and from
+main sequence winds in quadrature. $\vwO$ from SNe Ia's depends on the rate of mass loss ($\eta$), which is
+in turn a function of $t_{\rm age}$. This dependence is why the effective $\vwO$ increases with $\tage$ for
+large $\Mbh$.
+
+For very young stellar populations ($\tage \lsim 10^7$ years),  $\vwO\simeq 1000$ km/s due to contributions
+from line driven winds from high mass main sequence stars.
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{vw_eff.eps}
-\caption{\label{fig:vw_eff} Top panel: $\vwO$ vs.
-$\Mbh/\Msun$ assuming $\vwO$=100 km/s (from main sequence winds) for $\rs/\rIa<1$ and $\vwO$=500 km/s (from type Ia SNes) for $\rs/\rIa>1$.
-Bottom panel: $\rs/\rIa$ vs.
-$\Mbh/\Msun$ using heating prescription above.}
+\includegraphics[width=\columnwidth]{vw-contour.eps}
+\caption{\label{fig:vweff} Overall $\vwO$ for $\Mbh$-Stellar Age parameter space.}
 \end{figure}
@@
 %AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
+\end{enumerate}
 
@@
 
+\appendix
+\clearpage
+\section{Analytic Expression for the stagnation radius}
+\label{app:rs}
+\input{appendix}
+
+\section{Dependence of q on stellar age}
+\label{app:eta}
+\input{eta}
+
 \footnotesize{

### 2014-09-01 ms.tex
Some changes to intro.

@@
 In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.
-The accretion rate in turn has implications for rate of black hole growth.
+The accretion rate also has implications for rate of black hole growth.
 %AG:Perhaps need more detail here.
@@
 Both of the estimates suggest that there is an ample reservoir of gas to power active galactic nuclei in quiescent galaxies.
-This suggests that the lack of the AGN activity is due to the fact that the the accretion proceeds in a radiatively inefficient mode.
+This suggests that the lack of the AGN activity is due to the fact that the accretion proceeds in a radiatively inefficient mode.
 
@@
 
+We compare our calculated gas profiles to those inferred from Chandra X-ray observations by \citealt{AllenDunn+:2006a} and \citealt{RussellMcNamara+:2013a}.
+Additionally, we chack how well our results are able to reproduced relationships between $L_x$ and $\Mbh$.
+In performing these comparisons we hope to determine how well the gas environments of quiescent galaxies may be understood using the relatively well understood physics of stellar winds and supernova heating.
  %%AG--say something about x-ray observations.

### 2014-09-01 ms.tex
Filling in paragraphs

@@
 \newcommand{\Mbh}[1][]{M_{\bullet#1}}
+\newcommand{\Mbheight}{M_{\bullet,8}}
 \newcommand{\MbhNorm}{\frac{\Mbh}{10^8 \Msun}}
@@
 \newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
-\newcommand{\vwNormB}{\frac{\vwO}{500 \, {\rm km/s}}}
-\newcommand{\vwNormC}{\frac{\vwO}{500 \, {\rm km/s}}}
+\newcommand{\vwOFH}{v_{w,0,500}}
+\newcommand{\vwOFHexp}{\frac{\vwO}{500 \, {\rm km/s}}}
 
@@
 Supermassive black holes (SMBHs) are present in the centers of most,
-if not all nearby galaxies (see reviews by, e.g. \citealt{KormendyRichstone:1995a};
-\citealt{FerrareseFord:2005a}). Roughly $\sim 1\%$ of these manifest themselves as luminous Active Galactic Nuclei. However, quiescent black holes constitute a silent majority.
+if not all nearby galaxies (see reviews by,
+e.g. \citealt{KormendyRichstone:1995a};
+\citealt{FerrareseFord:2005a}). Roughly $\sim 1\%$ of these manifest
+themselves as luminous Active Galactic Nuclei. However, quiescent
+black holes constitute a silent majority.
 
-In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.
-The accretion rate also has implications for rate of black hole growth.
+In order to understand why most galaxies appear to be inactive, it is
+necessary to understand the gas environment of black holes, as the gas
+density around the black hole sets its accretion rate.  The accretion
+rate also has implications for rate of black hole growth.
 %AG:Perhaps need more detail here.
 
-Constraints on the SMBH accretion rates at the low end of the SMBH mass function also have implications for the black occupation fraction.
-For example, \citealt{MillerGallo+:2014a} used an observed relation between $\Mbh$ and nuclear x-ray luminosity $L_x$ to constrain the BH occupation fraction.
-However, they extrapolate (assuming a single power law) their observed relationship below their detection threshold.
-However, it is possible that the $L_x$-$\Mbh$ relationship steepens at smaller $\Mbh$, and thus the black hole occupation fraction could be underestimated at low $\Mbh$.
+Constraints on the SMBH accretion rates at the low end of the SMBH
+mass function also have implications for the black occupation
+fraction.  For example, \citealt{MillerGallo+:2014a} used an observed
+relation between $\Mbh$ and nuclear x-ray luminosity $L_x$ to
+constrain the BH occupation fraction.  However, they extrapolate
+(assuming a single power law) their observed relationship below their
+detection threshold.  However, it is possible that the $L_x$-$\Mbh$
+relationship steepens at smaller $\Mbh$, and thus the black hole
+occupation fraction could be underestimated at low $\Mbh$.
 %AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
 
-The gas environment also plays an important role in determining observables (light-curves, SEDs) from jetted tidal disruption events (TDEs).
-These are bright flares that occur when a star passes within the tidal disruption radius of the SMBH.
-A small fraction of   events are accompanied by the launch of a relativistic jet into the circumnuclear medium (CNM) of the host galaxy.
-As the jet propagates into the CNM, a reverse shock propagates towards the back of the jet, decelerating it.
-The CNM density profile will determine the final Lorentz factor of the jet.
-This in turn will strongly affect the duration of the observed synchotron radiation.
+The gas environment also plays an important role in determining
+observables (light-curves, SEDs) from jetted tidal disruption events
+(TDEs). These are bright flares that occur when a star passes within
+the tidal disruption radius of the SMBH. A small fraction of events
+are accompanied by the launch of a relativistic jet into the
+circumnuclear medium (CNM) of the host galaxy.  As the jet propagates
+into the CNM, a reverse shock propagates towards the back of the jet,
+decelerating it. The CNM density profile will determine the final
+Lorentz factor of the jet. This in turn will strongly affect the
+duration of the observed synchotron radiation.
 
-The gas in the vicinity of a black hole may come from several sources.
-\citealt{Ho:2009a} proposes three different mechanisms (1) Mass loss in winds (particularly from evolved stars) (2) Stellar-stellar collisions in dense environments (3) Tidal disruptions of stars.
-To estimate (a lower limit on the accretion rate), \citealt{Ho:2009a} calculates the Bondi accretion rate based on typical observed gas densities and temperatures taken from Chandra X-ray observations.
-A second estimate is obtained from the wind mass loss rate from the observed stellar densities.
-Both of the estimates suggest that there is an ample reservoir of gas to power active galactic nuclei in quiescent galaxies.
-This suggests that the lack of the AGN activity is due to the fact that the accretion proceeds in a radiatively inefficient mode.
+The gas in the vicinity of a black hole may come from several
+sources. \citealt{Ho:2009a} proposes three different mechanisms (1)
+Mass loss in winds (particularly from evolved stars) (2)
+Stellar-stellar collisions in dense environments (3) Tidal disruptions
+of stars. To estimate (a lower limit on the accretion rate),
+\citealt{Ho:2009a} calculates the Bondi accretion rate based on
+typical observed gas densities and temperatures taken from Chandra
+X-ray observations. A second estimate is obtained from the wind mass
+loss rate from the observed stellar densities. Both of the estimates
+suggest that there is an ample reservoir of gas to power active
+galactic nuclei in quiescent galaxies. This suggests that the lack of
+the AGN activity is due to the fact that the accretion proceeds in a
+radiatively inefficient mode.
 
-Previous studies used Chandra observations to show that the Bondi accretion power well-correlated with jet power \citep{AllenDunn+:2006a,FujitaKawakatu+:2014a}.
-In these studies temperature, and density information are inferred from Chandra x-ray observations, while the jet power is inferred from the energy required to inflate observed bubbles within the x-ray emitting gas.
+Previous studies used Chandra observations to show that the Bondi
+accretion power well-correlated with jet power
+\citep{AllenDunn+:2006a,FujitaKawakatu+:2014a}. In these studies
+temperature, and density information are inferred from Chandra x-ray
+observations, while the jet power is inferred from the energy required
+to inflate observed bubbles within the x-ray emitting gas.
 
-However, this approach has limitations.
-Due to resolution issues it is almost never possible to observationally determine the gas density at the black sphere of influence, and such studies are forced to extrapolate observed gas temperatures and densities to smaller scales.
-In fact, the temperature profile is assumed to be flat inside of the Bondi radius.
-In reality, the cusp in the velocity dispersion near the SMBH, should cause a cusp in the gas temperature profile (assuming the kinetic energy of stellar winds is efficiently themalized in shocks).
+However, this approach has limitations. Due to resolution issues it is
+almost never possible to observationally determine the gas density at
+the black sphere of influence, and such studies are forced to
+extrapolate observed gas temperatures and densities to smaller scales.
+In fact, the temperature profile is assumed to be flat inside of the
+Bondi radius.  In reality, the cusp in the velocity dispersion near
+the SMBH, should cause a cusp in the gas temperature profile (assuming
+the kinetic energy of stellar winds is efficiently themalized in
+shocks).
 %%AG-give sense of scale.
 
-Another approach to constraining the gas density around an SMBH is to go from a stellar mass loss rate (motivated by observed stellar densities) to a steady-state gas profile.
-This approach was taken by \citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}.
+Another approach to constraining the gas density around an SMBH is to
+go from a stellar mass loss rate (motivated by observed stellar
+densities) to a steady-state gas profile. This approach was taken by
+\citealt{Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}.
 
-%In this study we perform hydrodynamic modeling to solve for the steady-state gas density, temperature and velocity profiles near the SMBH sphere of influence, for a sample of nearby, quiescent galaxies.
-We a adopt the model used by \cite{Quataert:2004a} for the galactic center: gas is supplied by stellar winds, which collide, shock heat, and thermalize.
-We take the same approach.
-To the best of our knowledge a systematic study of the parameter space of central galaxy properties.
-Thus, we compute central density profiles for a broad sample of galaxies from \citealt{WangMerritt:2004a}--henceforward \citetalias{WangMerritt:2004a}.
-This allows us to relate the central stellar properties (e.g.
-the slope of the stellar density) to the central gas properties.
+% In this study we perform hydrodynamic modeling to solve for the
+% steady-state gas density, temperature and velocity profiles near the
+% SMBH sphere of influence, for a sample of nearby, quiescent
+% galaxies. We a adopt the model used by \cite{Quataert:2004a} for the
+% galactic center: gas is supplied by stellar winds, which collide,
+% shock heat, and thermalize.
+We take the same approach. To the best of our knowledge a systematic
+study of the parameter space of central galaxy properties. Thus, we
+compute central density profiles for a broad sample of galaxies from
+\citealt{WangMerritt:2004a}--henceforward
+\citetalias{WangMerritt:2004a}.  This allows us to relate the central
+stellar properties (e.g. the slope of the stellar density) to the
+central gas properties.
 
-For each galaxy in our chosen sample, we find a steady state gas profile.
-Typically an inflow-outflow structure is established.
-The stellar ejecta inside of the stagnation radius ($\rs$) will be accreted, while that outside $\rs$ will be driven out with the outflow.
-It is often assumed that the gas properties at the Bondi radius, $\rb$ set the accretion rate.
-However, physically it is really $\rs$ which sets the accretion rate.
-Typically this lies within a factor of a few of the $\rb$.
-This means that with perfect knowledge of the gas profile the $\Mdotb$ is typically a good approximation to the actual accretion rate $\Mdot$.
-However, using extrapolations of the observed gas temperature and density to estimate $\Mdot$ may cause systematic order of magnitude errors in the inferred  accretion rate.
+For each galaxy in our chosen sample, we find a steady state gas
+profile. Typically an inflow-outflow structure is established. The
+stellar ejecta inside of the stagnation radius ($\rs$) will be
+accreted, while that outside $\rs$ will be driven out with the
+outflow.  It is often assumed that the gas properties at the Bondi
+radius, $\rb$ set the accretion rate. However, physically it is really
+$\rs$ which sets the accretion rate. Typically this lies within a
+factor of a few of the $\rb$.  This means that with perfect knowledge
+of the gas profile the $\Mdotb$ is typically a good approximation to
+the actual accretion rate $\Mdot$.  However, using extrapolations of
+the observed gas temperature and density to estimate $\Mdot$ may cause
+systematic order of magnitude errors in the inferred accretion rate.
 
-The location of $\rs$ and hence the accretion rate is  quite sensitive to the assumed heating rate.
-Physically, the heating rate of the gas would vary from galaxy to galaxy.
-For example, SNe Ia may be a large source of energy for the gas.
-However, this will be only be the case for larger black holes for which the gas inflow time is smaller than the time between successive Ias.
-Thus, for smaller black holes, the effective gas heating rate may be considerably smaller.
-Thus, we investigate the effect of changing rate of energy injection on the gas density profiles.
+The location of $\rs$ and hence the accretion rate is quite sensitive
+to the assumed heating rate.  Physically, the heating rate of the gas
+would vary from galaxy to galaxy. For example, SNe Ia may be a large
+source of energy for the gas. However, this will be only be the case
+for larger black holes for which the gas inflow time is smaller than
+the time between successive Ias. Thus, for smaller black holes, the
+effective gas heating rate may be considerably smaller. Thus, we
+investigate the effect of changing rate of energy injection on the gas
+density profiles.
 
-We compare our calculated gas profiles to those inferred from Chandra X-ray observations by \citealt{AllenDunn+:2006a} and \citealt{RussellMcNamara+:2013a}.
-Additionally, we chack how well our results are able to reproduced relationships between $L_x$ and $\Mbh$.
-In performing these comparisons we hope to determine how well the gas environments of quiescent galaxies may be understood using the relatively well understood physics of stellar winds and supernova heating.
+We compare our calculated gas profiles to those inferred from Chandra
+X-ray observations by \citealt{AllenDunn+:2006a} and
+\citealt{RussellMcNamara+:2013a}. Additionally, we chack how well our
+results are able to reproduced relationships between $L_x$ and
+$\Mbh$. In performing these comparisons we hope to determine how well
+the gas environments of quiescent galaxies may be understood using the
+relatively well understood physics of stellar winds and supernova
+heating.
  %%AG--say something about x-ray observations.
@@
 \section{Sample}
-We start with a sample of 61 galaxies from \citetalias{WangMerritt:2004a}, as subset of a larger sample of galaxies from \citealt{FaberTremaine+:1997a}.
-These are nearby elliptical galaxies, observed with the Hubble WFPC2.
+We start with a sample of 61 galaxies from
+\citetalias{WangMerritt:2004a}, as subset of a larger sample of
+galaxies from \citealt{FaberTremaine+:1997a}. These are nearby
+elliptical galaxies, observed with the Hubble WFPC2.
 
-We focus on elliptical galaxies to isolate the effect of mass loss from a relatively old stellar population, avoiding additional gas flowing in from star formation on larger scales.
+We focus on elliptical galaxies to isolate the effect of mass loss
+from a relatively old stellar population, avoiding additional gas
+flowing in from star formation on larger scales.
 
-For each galaxy in the sample we take the surface brightness parameterization given in Table 1 of  \citetalias{WangMerritt:2004a}. The parameterization is a Nuker law
+For each galaxy in the sample we take the surface brightness
+parameterization given in Table 1 of
+\citetalias{WangMerritt:2004a}. The parameterization is a Nuker law
 
@@
 
-This is a broken power law which transitions from an inner power law slope, $\gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.
-The corresponding (spherically symmetric) stellar density, $\rhostar\sim r^{-1-\gamma}$ for $r \ll \rb$ and  $\rhostar\sim r^{-1-\beta}$ for $r \ll \rb$.
-$\gamma\simeq1$ for cusp galaxies, while $\gamma\simeq0$ for core galaxies.
+This is a broken power law which transitions from an inner power law
+slope, $\gamma$, to an outer power law slope, $\beta$, at a break
+radius, $\rb$.  The corresponding (spherically symmetric) stellar
+density, $\rhostar\sim r^{-1-\gamma}$ for $r \ll \rb$ and
+$\rhostar\sim r^{-1-\beta}$ for $r \ll \rb$.  $\gamma\simeq1$ for cusp
+galaxies, while $\gamma\simeq0$ for core galaxies.
 %AG:Is there a systematic dependence of beta on galaxy type$.
 
-From the surface brightness profile, we follow the same procedure as \citetalias{WangMerritt:2004a} to compute the spatial stellar density and stellar mass profile, both of which are used in our model.
+From the surface brightness profile, we follow the same procedure as
+\citetalias{WangMerritt:2004a} to compute the spatial stellar density
+and stellar mass profile, both of which are used in our model.
 
-%%AG--some discussion of alternate parameterizations.
-My intuition is that for our purposes the parameterization should not matter.
-But some discussion of alternate possibilities could prevent Alistar Graham from yelling at us.
+%% AG--some discussion of alternate parameterizations.  My intuition
+%% is that for our purposes the parameterization should not
+%% matter. But some discussion of alternate possibilities could
+%% prevent Alistar Graham from yelling at us.
 
@@
 \label{sec:model}
-We use the same model as \citealt{Quataert:2004a} to find a steady state gas density near the SMBH for each of the galaxies within our sample.
-Gas is supplied by winds from the stellar population in the galactic center.
-Assuming a rate of mass injection, $q$, spherical symmetry and an ideal gas equation of state.
+We use the same model as \citealt{Quataert:2004a} to find a steady
+state gas density near the SMBH for each of the galaxies within our
+sample.  Gas is supplied by winds from the stellar population in the
+galactic center. Assuming a rate of mass injection, $q$, spherical
+symmetry and an ideal gas equation of state.
 
@@
 
-These or similar equations have been solve many times in the literature (e.g.
-\citealt{HolzerAxford:1970a,Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}).
-\citealt{ShcherbakovWong+:2014a} adds additional terms to account for thermal conduction and radiative cooling.
-However, we find that radiative cooling may be neglected for a large portion of our parameter space--\S~\ref{sec:cooling}.
-Additionally thermal conduction may be cut off by magnetic field lines--\S~\ref{sec:conduction}
+These or similar equations have been solve many times in the
+literature (e.g. \citealt{HolzerAxford:1970a,Quataert:2004a,De-ColleGuillochon+:2012a,ShcherbakovWong+:2014a}). \citealt{ShcherbakovWong+:2014a}
+adds additional terms to account for thermal conduction and radiative
+cooling. However, we find that radiative cooling may be neglected for
+a large portion of our parameter space--\S~\ref{sec:cooling}.
+Additionally thermal conduction may be cut off by magnetic field
+lines--\S~\ref{sec:conduction}
 
-$q$ represent the rate of injection of gas mass per unit volume, and is derived from the stellar density, $\rho_*$, using
+$q$ represent the rate of injection of gas mass per unit volume, and
+is derived from the stellar density, $\rho_*$, using
 
@@
 
-%{\bf NCS: here is some added detail about the role of stellar mass functions in the model}
+% {\bf NCS: here is some added detail about the role of stellar mass
+% functions in the model}
 
-% if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.
-Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?
-Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.
-Crudely approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} < 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss on the main sequence), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
+% if we consider different star formation scenarios (for example,
+% continuous star formation) or different IMFs, it will change.  Once
+% these free parameters are specified, however, we can answer an
+% important question: do young stellar populations increase or
+% decrease the SMBH feeding rate $\dot{M}$?  Clearly, $\eta(t)$ is
+% larger for young stellar populations, but these stars also have high
+% wind velocities that diminish the stagnation radius.  Crudely
+% approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} <
+% 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} >
+% 10M_{\odot}$ (motivated by the transition from dust-driven wind loss
+% on the AGB to line-driven wind loss on the main sequence), we can
+% employ the relation $\dot{M} \propto \eta(t) r_{\rm
+% s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_*
+% \propto r^{-\Gamma}$) to determine the impact of stellar ``youth''
+% on SMBH feeding rates.
 %
@@
 &\rs=\frac{7}{2}\frac{G \Mbh}{n \vw^2}\\
-&\simeq 6 \, \pc \left(\MbhNorm\right) \left(\vwNormB\right)^{-2}
+&\simeq 6 \, \pc \left(\MbhNorm\right) \left(\vwOFH\right)^{-2}
 \label{eq:stag_simple}
@@
 \[
-\dot{M}
+\dot{M}=
 \begin{cases}
-   1.5 \time 10^{-3}  \left(\MbhNorm\right)^{1.9} \left(\vwNormB\right)^{-4} \Msun \, \pyear& \text{for core galaxies} \\
-   3.3 \times 10^{-3}   & \text{for cusp galaxies}     
+   1.5 \times 10^{-3}  \left(\Mbheight\right)^{1.9} \left(\vwOFH\right)^{-4} \Msun \, \pyear& \text{for core galaxies} \\
+   3.3 \times 10^{-3} \left(\Mbheight\right)^{1.4} \left(\vwOFH\right)^{-2}  \Msun \, \pyear  & \text{for cusp galaxies} 
 \end{cases}
-\label{eq:cooling}
+\label{eq:mdot_analytic}
 \]
@@
 
-%%AG-Apparently even in the low heating case, it is still possible to an outflow (from the analytic results above the gas density must be quite steep in this case).
-However, at low heating we will probably become subject to a cooling instablity.
-%%AG-I believe that in the case of core galaxy, the negative root of the quadratic should be taken...
+%% AG-Apparently even in the low heating case, it is still possible to
+%% an outflow (from the analytic results above the gas density must be
+%% quite steep in this case). However, at low heating we will probably
+%% become subject to a cooling instablity.  AG-I believe that in the
+%% case of core galaxy, the negative root of the quadratic should be
+%% taken...
 
@@
 
-We show the numerical results for $\x$ vs.
-$\eta$ in the top panel of Figure~\ref{fig:stag}.
-The three different colors represent the three different chosen values of $\vwO$.
-The square points represent cusp galaxies, whereas the triangles represent core galaxies.
-The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.
+We show the numerical results for $\x$ vs. $\eta$ in the top panel of
+Figure~\ref{fig:stag}.  The three different colors represent the three
+different chosen values of $\vwO$. The square points represent cusp
+galaxies, whereas the triangles represent core galaxies.  The solid
+line is a power law fit through the cusp galaxies, while the dotted
+line is a power law fit through the core galaxies.
 
-Using the slope of the density profile, at the stagnation radius we may use Equation~\ref{eq:stag_analytic} to compute $\x$ analytically.
-We plot the fractional difference between the numerical and analytic results for $\x$ for each galaxy in the bottom panel of Figure~\ref{fig:stag}.
-Generally, the agreement is quite good (especially for $\vwO$=1000 km/s and $\vwO$=500 km/s), providing a useful check of the numerical results.
+Using the slope of the density profile, at the stagnation radius we
+may use Equation~\ref{eq:stag_analytic} to compute $\x$
+analytically. We plot the fractional difference between the numerical
+and analytic results for $\x$ for each galaxy in the bottom panel of
+Figure~\ref{fig:stag}.  Generally, the agreement is quite good
+(especially for $\vwO$=1000 km/s and $\vwO$=500 km/s), providing a
+useful check of the numerical results.
 
@@
 \includegraphics[width=\columnwidth]{profiles.eps}
-\caption{\label{fig:profiles}Radial for three different galaxies: NGC1172, NGC4478, and NGC3115. Solid curves correspond to $v_w$=1000 km/s.
-The Dot-dashed curve corresponds to $v_w$=200 km/s. Top panel: Density; 
-Middle Panel: Temperature; Bottom Panel: X-ray luminosity enclosed within radius $r$.}
+\caption{\label{fig:profiles}Radial for three different galaxies:
+  NGC1172, NGC4478, and NGC3115. Solid curves correspond to $v_w$=1000
+  km/s.  The Dot-dashed curve corresponds to $v_w$=200 km/s. Top
+  panel: Density; Middle Panel: Temperature; Bottom Panel: X-ray
+  luminosity enclosed within radius $r$.}
 \end{figure}
@@
 \subsection{Heating}
-We now discuss potential sources of heating and discuss how different physical sources of heating would lead to different values of $\vwO$.
-For each heating source  from the heating rate per unit volume $e$ we may estimate the corresponding $\vwO$, using
+We now discuss potential sources of heating and discuss how different
+physical sources of heating would lead to different values of
+$\vwO$. For each heating source from the heating rate per unit volume
+$e$ we may estimate the corresponding $\vwO$, using
 
@@
 
-We estimate the value of the $\vwO$ for different physical heating sources below.
+We estimate the value of the $\vwO$ for different physical heating
+sources below.
 
 \begin{enumerate}
-\item \emph{Stellar winds} The contribution to the heating rate from the red giant winds themselves will be negligible, as red giants have wind velocities $\lsim 40$ km/s.
+\item \emph{Stellar winds} The contribution to the heating rate from
+  the red giant winds themselves will be negligible, as red giants
+  have wind velocities $\lsim 40$ km/s.
 
-Although red giant winds dominate the mass budget, winds from main sequence stars may make a significant contribution to the energy budget, with wind velocities $\sim 100-150$ km/s \citep{NaimanSoares-Furtado+:2013a}.
+  Although red giant winds dominate the mass budget, winds from main
+  sequence stars may make a significant contribution to the energy
+  budget, with wind velocities $\sim 100-150$ km/s
+  \citep{NaimanSoares-Furtado+:2013a}.
 
-\item \emph{MS Pulsars} 
-The spin down power of millisecond pulsars (MSPs) could potentially be an important heating source. Assuming a spin-down luminosity $L_{\rm sd}$ and $n_{\rm msp}$ MSPs per unit mass
+\item \emph{MS Pulsars} The spin down power of millisecond pulsars
+  (MSPs) could potentially be an important heating source. Assuming a
+  spin-down luminosity $L_{\rm sd}$ and $n_{\rm msp}$ MSPs per unit
+  mass
 
@@
 
-There may be as many 30,000 MSPs in the Milky way, which would give  $n_{\rm msp}\simeq3 \times 10^{-41} $ MSPs g$^{-1}$.
-Even if we optimistically take $L_{\rm sd}\simeq 10^{35}$ ergs/s, and $\eta$=0.1, we would get $\vwO\simeq40$ km/s, which means heating by MSPs is negligible.
+There may be as many 30,000 MSPs in the Milky way, which would give
+$n_{\rm msp}\simeq3 \times 10^{-41} $ MSPs g$^{-1}$. Even if we
+optimistically take $L_{\rm sd}\simeq 10^{35}$ ergs/s, and $\eta$=0.1,
+we would get $\vwO\simeq40$ km/s, which means heating by MSPs is
+negligible.
 
@@
 
-\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}$, and the SNe rate,  $R_{\rm Ia}$
+\item \emph{Type Ia SNe} From he energy injected per Ia SNe,
+  $E_{\rm Ia}$, and the SNe rate, $R_{\rm Ia}$
 
@@
 
- Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which gives $\vwO\simeq 230 \, \eta^{-1/2}$ km/s (For $\eta=0.1$ this corresponds to $\vwO\simeq$ 500 km/s.
+Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs
+and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which
+gives $\vwO\simeq 230 \, \eta^{-1/2}$ km/s (For $\eta=0.1$ this
+corresponds to $\vwO\simeq$ 500 km/s.
  %Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.
 
-As noted in \citealt{ShcherbakovWong+:2014a}, SNe energy injection cannot necessarily be treated as constant throughout  time and space, since the flow time-scale may be short compared to the time between successive SNe Ia.
+ As noted in \citealt{ShcherbakovWong+:2014a}, SNe energy injection
+ cannot necessarily be treated as constant throughout time and space,
+ since the flow time-scale may be short compared to the time between
+ successive SNe Ia.
 
-There will be some radius, $\rIa$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.
-If the stagnation radius ($\rs$) of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$
+There will be some radius, $\rIa$, where the dynamical timescale of
+the flow becomes comparable to the time between successive Type Ia
+SNe.  If the stagnation radius ($\rs$) of the flow is outside of
+$\rIa$ then SNes will provide a steady contribution to $\vwO$
 
@@
 \begin{align}
- t_{\rm dyn} \sim r/\sigma \sim G \Mstar/\sigma^3 \sim 5 \times 10^4 \Mseight \sigma_{200}^{-3} \; {\rm yrs}.
+  t_{\rm dyn} \sim r/\sigma \sim G \Mstar/\sigma^3 \sim 5 \times 10^4
+  \Mseight \sigma_{200}^{-3} \; {\rm yrs}.
 \end{align}
@@
 \begin{align}
- r_{\rm Ia} \sim G \Mstar{}_{,\rm Ia}/\sigma^2 \sim 4 \sigma_{200}^{-1/2} \; {\rm pc}
+  r_{\rm Ia} \sim G \Mstar{}_{,\rm Ia}/\sigma^2 \sim 4
+  \sigma_{200}^{-1/2} \; {\rm pc}
 \end{align}
 
-The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant.
-For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.
-Above $\sim10^8 \Msun$ SNes will represent an important contribution to the overall heating.
-%Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds.
-On the other hand, for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe.
-These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
+The stagnation radius scales linearly with $\Mbh$ (see
+Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly
+constant. For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will
+not contribute to the $\vwO$.  Above $\sim10^8 \Msun$ SNes will
+represent an important contribution to the overall heating.
+% Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with
+% heating mostly coming from main sequence winds. On the other hand,
+% for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with
+% the main contribution coming from type Ia SNe. These two regimes are
+% illustrated in Figure~\ref{fig:vw_eff}.
 %\end{enumerate}
 
-\item \emph{Overall Heating Rate}
-The overall value of $\vwO$ has contributions from Type Ia SNes  and main sequence winds.  The relative
-contributions will depend on both the age of the stellar population, $t_{\rm age}$ and $\Mbh$.  This is
-illustrated in Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe Ia will not contribute to 
-$\vwO$ as the flow time scale is short compared to $t_{\rm Ia}$, and the heating is dominated by main
-sequence winds (with $\vwO\simeq 100$ km/s).  On the other hand, for $\Mbh \gsim 10^8 \Msun$, heating
-from Ias becomes important, as $\rs>\rIa$.  In this regime, we add the $\vwO$ values from SNe Ias and from
-main sequence winds in quadrature. $\vwO$ from SNe Ia's depends on the rate of mass loss ($\eta$), which is
-in turn a function of $t_{\rm age}$. This dependence is why the effective $\vwO$ increases with $\tage$ for
-large $\Mbh$.
+\item \emph{Overall Heating Rate} The overall value of $\vwO$ has
+  contributions from Type Ia SNes and main sequence winds.  The
+  relative contributions will depend on both the age of the stellar
+  population, $t_{\rm age}$ and $\Mbh$.  This is illustrated in
+  Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe
+  Ia will not contribute to $\vwO$ as the flow time scale is short
+  compared to $t_{\rm Ia}$, and the heating is dominated by main
+  sequence winds (with $\vwO\simeq 100$ km/s).  On the other hand, for
+  $\Mbh \gsim 10^8 \Msun$, heating from Ias becomes important, as
+  $\rs>\rIa$.  In this regime, we add the $\vwO$ values from SNe Ias
+  and from main sequence winds in quadrature. $\vwO$ from SNe Ia's
+  depends on the rate of mass loss ($\eta$), which is in turn a
+  function of $t_{\rm age}$. This dependence is why the effective
+  $\vwO$ increases with $\tage$ for large $\Mbh$.
 
-For very young stellar populations ($\tage \lsim 10^7$ years),  $\vwO\simeq 1000$ km/s due to contributions
-from line driven winds from high mass main sequence stars.
+For very young stellar populations ($\tage \lsim 10^7$ years),
+$\vwO\simeq 1000$ km/s due to contributions from line driven winds
+from high mass main sequence stars.
 
@@
 
-%AG-I am not comfortable saying type Ia SNe's don't contribute to heating for smaller mass BHs.
-If the cooling time for the SNe is long then it would be wrong to ignore the SNe contribution.
-The difference would be that the SNe heating would just be less steady.
-%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
+% AG-I am not comfortable saying type Ia SNe's don't contribute to
+% heating for smaller mass BHs. If the cooling time for the SNe is
+% long then it would be wrong to ignore the SNe contribution. The
+% difference would be that the SNe heating would just be less steady.
+% AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
 \end{enumerate}
@@
 \subsection{Mass accretion rate}
-For each of our solutions, we may calculate the accretion rate $\dot{M}$ onto the SMBH.
-We show $\Mdote$ vs.
-$\Mbh$ as a function of black hole mass for our three  chosen values of the $\vwO$ (200 km/s, 500 km/s, and 1000 km/s).
-The results are shown in Figure~\ref{fig:mdot_mass}.
-Note that $\dot{M}\sim\vwO^{-2}$ for a cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy.
-Thus, the mass accretion rate will be a sensitive function of the assumed heating rate.
+For each of our solutions, we may calculate the accretion rate
+$\dot{M}$ onto the SMBH. We show $\Mdote$ vs. $\Mbh$ as a function of
+black hole mass for our three chosen values of the $\vwO$ (200 km/s,
+500 km/s, and 1000 km/s). The results are shown in
+Figure~\ref{fig:mdot_mass}.  Note that $\dot{M}\sim\vwO^{-2}$ for a
+cusp galaxy and $\dot{M}\sim\vwO^{-4}$ for a core galaxy. Thus, the
+mass accretion rate will be a sensitive function of the assumed
+heating rate.
 %%AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
@@
 
-The accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$, while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.
-This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag}).
-Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.
-For $\vwO=1000$ km/s, core galaxies have a smaller accretion rate for a given black hole mass.
+The accretion rate is proportional to the stellar mass enclosed inside
+of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$,
+while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.  This steeper
+dependence is enough to offset the tendency for core galaxies to have
+a larger $\rs/\rsoi$ for fixed $\eta$ (see
+Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core galaxies
+would have a smaller $\dot{M}$ than cusp galaxies.  For $\vwO=1000$
+km/s, core galaxies have a smaller accretion rate for a given black
+hole mass.
 
-We find there is a trend of $\eddr$ increasing towards higher black hole masses.
-However, previous work  suggests a downsizing trend: for quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.
-If $L_X\sim\dot{M}^2$, this would suggest $\eddr\sim \Mbh^{-0.6}$.
-In contrast for fixed $\vwO$ and $\eta$ we obtain that $\eddr\sim \Mbh^{0.5-1}$.
-One possible solution is that $\eta$ decreases with $\Mbh$.
-$\dot{M}$ scales linearly with $\eta$, so we would need to have $\eta\sim \Mbh^{-1}$ to explain the observed downsizing trend.
+We find there is a trend of $\eddr$ increasing towards higher black
+hole masses. However, previous work suggests a downsizing trend: for
+quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq
+0.7-0.8$ \citep{MillerGallo+:2014a}. If $L_X\sim\dot{M}^2$, this would
+suggest $\eddr\sim \Mbh^{-0.6}$. In contrast for fixed $\vwO$ and
+$\eta$ we obtain that $\eddr\sim \Mbh^{0.5-1}$. One possible solution
+is that $\eta$ decreases with $\Mbh$. $\dot{M}$ scales linearly with
+$\eta$, so we would need to have $\eta\sim \Mbh^{-1}$ to explain the
+observed downsizing trend.
 
@@
 \subsection{Comparison with observations}
-\citealt{AllenDunn+:2006a} use Chandra x-ray observations to infer the temperature and density profiles for nine nearby x-ray luminous elliptical galaxies.
-Five of the galaxies in their sample overlap with that in \citetalias{WangMerritt:2004a}.
+\citealt{AllenDunn+:2006a} use Chandra x-ray observations to infer the
+temperature and density profiles for nine nearby x-ray luminous
+elliptical galaxies.  Five of the galaxies in their sample overlap
+with that in \citetalias{WangMerritt:2004a}.
 
-We may compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.
-Note that we we have two free parameters ($\eta$ and $\vwO$ in our model and thus we can can always match $T$ and $\rho$ at least one point.
-We generally find that $\vwO=500$ km/s (as would be expected from SNe Ia) gives rough agreement with the observed temperatures.
-Thus, we choose $\vwO=500$ km/s.
-We choose an $\eta$ so that our solution would be consistent with the observed density profiles.
-The comparison is shown in Figure~\ref{fig:allen_compare}.
+We may compare our results for the $T$ and $\rho$ profiles with those
+inferred from observations for the overlapping galaxies.  Note that we
+we have two free parameters ($\eta$ and $\vwO$ in our model and thus
+we can can always match $T$ and $\rho$ at least one point.  We
+generally find that $\vwO=500$ km/s (as would be expected from SNe Ia)
+gives rough agreement with the observed temperatures.  Thus, we choose
+$\vwO=500$ km/s.  We choose an $\eta$ so that our solution would be
+consistent with the observed density profiles. The comparison is shown
+in Figure~\ref{fig:allen_compare}.
 %%AG-The chosen properties, in particular eta may be summarized in a table.
@@
 \item \emph{NGC4486} %eta=0.2
-On scales of $\sim1$ kpc the density profile in \citealt{AllenDunn+:2006a}  is shallower than in our model.
-Our model has a break in the gas density at $\sim 300$ pc--near the location of the Nuker break radius for this galaxy at 560 pc.
-There is an observed break in the density, but on a scale of a few kpc.
+  On scales of $\sim1$ kpc the density profile in
+  \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
+  has a break in the gas density at $\sim 300$ pc--near the location
+  of the Nuker break radius for this galaxy at 560 pc. There is an
+  observed break in the density, but on a scale of a few kpc.
 
-In contrast to a naive extrapolation of the observed $T$ and $\rho$ to smaller scales, our models have $T$ and $\rho$ monotonically increasing towards the galactic center.
-The increase in $T$ is due to the increased velocity dispersion (and thus increased heating) towards the galactic center.
+  In contrast to a naive extrapolation of the observed $T$ and $\rho$
+  to smaller scales, our models have $T$ and $\rho$ monotonically
+  increasing towards the galactic center. The increase in $T$ is due
+  to the increased velocity dispersion (and thus increased heating)
+  towards the galactic center.
 \end{itemize}
@@
 \label{sec:cooling}
-In our models stellar winds collide, shock heat, and thermalize.
-The rate of energy injection (parameterized by $\vwO$) sets a characteristic temperature--see Equation~\ref{eq:tstag}.
-For a given amount of injected mass, the energy input from shock heating should be equal to the enthalpy of the gas.
+In our models stellar winds collide, shock heat, and thermalize. The
+rate of energy injection (parameterized by $\vwO$) sets a
+characteristic temperature--see Equation~\ref{eq:tstag}.  For a given
+amount of injected mass, the energy input from shock heating should be
+equal to the enthalpy of the gas.
 
-The gas should radiatively cool as well--either from metal line cooling for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim 2\times 10^7$ K.
-However, if the cooling rate is much smaller than the rate of energy injection then radiative cooling may be safely neglected.
+Gas should radiatively cool as well--either from metal line cooling
+for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim
+2\times 10^7$ K.  However, if the cooling rate is much smaller than
+the rate of energy injection then radiative cooling may be safely
+neglected.
 
-For each of our solutions we compare the radiative cooling rate, $C$ to the heating rate $H=q \vw^2/2$. If $H/C \gg  1$ then cooling may be neglected. We take
+For each of our solutions we compare the radiative cooling rate, $C$
+to the heating rate $H=q \vw^2/2$. If $H/C \gg 1$ then cooling may be
+neglected. We take
 
@@
 
-Where $n$ is the number density and $\Lambda(T)$ is the cooling function. We approximate $\Lambda(T)$ as piece-wise power law (fitted for solar metallicity--see Figure 34.1 in \cite{Draine:2011a})
+Where $n$ is the number density and $\Lambda(T)$ is the cooling
+function. We approximate $\Lambda(T)$ as piece-wise power law (fitted
+for solar metallicity--see Figure 34.1 in \cite{Draine:2011a})
 %cite Draine
@@
 
-Note $C\propto n^2\propto \eta^2$.
-On the other hand, $H \propto q  \propto \eta$.
-Thus, the ratio $H/C$ will depend upon the free parameter $\eta$.
-We plot $H/C$ for all of our profiles for our fiducial $\eta=1$.
+Note $C\propto n^2\propto \eta^2$. On the other hand, $H \propto q
+\propto \eta$. Thus, the ratio $H/C$ will depend upon the free
+parameter $\eta$. We plot $H/C$ for all of our profiles for our
+fiducial $\eta=1$.
 
@@
 
-For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that radiative cooling may be safely neglected.
-With a few exceptions this is also true for $\vwO$=500 km/s.
-However, for $\vwO$=200 km/s cooling may be quite important.
+For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling},
+that radiative cooling may be safely neglected. With a few exceptions
+this is also true for $\vwO$=500 km/s.  However, for $\vwO$=200 km/s
+cooling may be quite important.
 
-For small $\eta$ the effects of cooling will be less pronounced.
-For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .
-Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling.
-$\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.
+For small $\eta$ the effects of cooling will be less pronounced. For
+each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in
+Table .  Roughly speaking, this is the maximum $\eta$ for which it
+would be safe to ignore cooling. $\eta$ depends on the age of the
+stellar population, and will realistically vary between $\sim 0.1$ and
+$\sim 1$.
+
+For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that rad
 

### 2014-09-02 eta.tex
Fixing typos in manuscript and commiting both appendices.

We now describe the rate of start formation $q$ varies with the age of the stellar population.

If we assume that a stellar population forms impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any future time $t$ is given by 
\begin{equation}
f(t) =\frac{ \int_{m_0}^{m_{\rm max}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
\end{equation}
where 
\begin{equation}
m_{\rm max}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
\end{equation}
For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
\begin{equation}
f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
\end{equation}
%{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
\begin{equation}
q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm max}(t)) m_{\rm max}(t) \frac{df}{dt},
\end{equation}
where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm max}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
\begin{equation}
q(t) = \frac{\rho_*}{\th} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
\end{equation}
This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$;

### 2014-09-02 ms.tex
Fixing typos in manuscript and commiting both appendices.

@@
 \newcommand{\tage}{t_{\rm age}}
+\renewcommand{\th}{t_h}
 
@@
 
-\author[Generozov, Metzger, \& Stone]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Brian~D.~Metzger, Nicholas Stone$\footnotemark[1]$\\
+\author[Generozov, Metzger, \& Stone]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Brian~D.~Metzger, Nicholas Stone\\
 Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}
@@
 the time between successive Ias. Thus, for smaller black holes, the
-effective gas heating rate may be considerably smaller. Thus, we
+effective gas heating rate may be considerably smaller. We
 investigate the effect of changing rate of energy injection on the gas
@@
 \citealt{RussellMcNamara+:2013a}. Additionally, we chack how well our
-results are able to reproduced relationships between $L_x$ and
-$\Mbh$. In performing these comparisons we hope to determine how well
-the gas environments of quiescent galaxies may be understood using the
-relatively well understood physics of stellar winds and supernova
-heating.
+results are able to reproduced relationships between $L_x$ and $\Mbh$
+in \citealt{MillerGallo+:2014a}. In performing these comparisons we
+hope to determine how well the gas environments of quiescent galaxies
+may be understood using the relatively well understood physics of
+stellar winds and supernova heating.
  %%AG--say something about x-ray observations.
@@
 \section{Solutions}
-\subsection{Analytics: Flow properties and $\rs$}
+\subsection{Analytics: Flow properties at $\rs$}
 It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density (at $\rs$) $n$.
@@
 
-We may also write an (implicit) analytic expression for $\rs$ itself. Let $\omega=\Mstar(\rs)/\Mbh$ and  $\eta=v_{w,0}/\sigma_{\rm soi}$.
+We may also write an (implicit) analytic expression for $\rs$
+itself. Let  $\eta=v_{w,0}/\sigma_{\rm soi}$. Then
 
 \begin{align}
-\x=\frac{1}{\eta^2 n}\left[ (1+\omega)\left(A-\frac{n}{2}\right)-B\right]
+\x=\frac{1}{\eta^2 n}\left[ (1+\Mstar(\rs)/\Mbh)\left(A-\frac{n}{2}\right)-B\right]
 \label{eq:stag_analytic}
@@
 
-When $\Mstar << \Mbh$ at the stagnation radius, the relationship between $\rs$ and $\vw$ is greatly simplified.
+Where A and B are are constants, which depend on the nuker $\gamma$
+and the adiabatic index of the gas (see Appendix~\ref{app:rs})  $\Mstar << \Mbh$ at the stagnation radius, the relationship between $\rs$ and $\vw$ is greatly simplified.
 
@@
 
-\[
-\dot{M}=
+\begin{align}
+\dot{M}\simeq
 \begin{cases}
-   1.5 \times 10^{-3}  \left(\Mbheight\right)^{1.9} \left(\vwOFH\right)^{-4} \Msun \, \pyear& \text{for core galaxies} \\
-   3.3 \times 10^{-3} \left(\Mbheight\right)^{1.4} \left(\vwOFH\right)^{-2}  \Msun \, \pyear  & \text{for cusp galaxies} 
+   1.5 \times 10^{-3}  \left(\Mbheight\right)^{1.9}
+   \left(\vwOFH\right)^{-4} \eta \Msun \, \pyear& \text{for core galaxies} \\
+   3.3 \times 10^{-3} \left(\Mbheight\right)^{1.4}
+   \left(\vwOFH\right)^{-2} \eta \Msun \, \pyear  & \text{for cusp
+     galaxies} 
  \end{cases}
 \label{eq:mdot_analytic}
-\]
+\end{align}
 
-Finally, we may estimate the $\rho$ at $\rs$, using
+In our model the accretion onto the black hole may be approximated as
+the gas mass enclosed inside $\rs$ divided by the free-fall time at $\rs$.
 
-\begin{equation}
-\rho(\rs)\simeq q(\rs) \tff
-\end{equation}
+\begin{align}
+&\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}(\rs)}
+\label{eq:mdot_gas}
+\end{align}
+
+Finally, using Equations~\ref{eq:tstag} and \ref{eq:mdot_analytic}, we
+may obtain a scaling relationship for $\rho(\rs)$.
+
+\begin{align}
+\rho(\rs)\simeq
+\begin{cases}
+2.5 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \eta \, {\rm g \, cm^{-3}}& \text{for   galaxies}\\
+5.5 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH    \eta \, {\rm g \,cm^{-3}} & \text{for cursp galaxies}
+\end{cases}
+\label{eq:rhors}
+\end{align}
 
 \subsection{Comparison with Bondi Accretion}
-The Bondi accretion rate, $\Mdotb$ is given by
+The Bondi accretion rate, $\Mdotb$ in terms of the Bondi radius $\rb=G
+M/c_s^2$ is
 
 \begin{align}
-\Mdotb=4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b)
+\Mdotb=4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b).
 \end{align}
 
-where $r_b=G M/c_s^2$.
-
-%%AG: I am not entirely comfortable with this approximation for the accretion rate. 
-In our model the accretion rate may be approximated as the mass enclosed with $\rs$ divided by the free-fall time.
+We may rewrite Equation~\ref{eq:mdot_gas} as follows
 
@@
 
-Where have set $n=1$.  At $\rs$ we have
+Where have set the power law slope of the gas density, $n$, to 1.  At $\rs$ we have
 
@@
   relative contributions will depend on both the age of the stellar
-  population, $t_{\rm age}$ and $\Mbh$.  This is illustrated in
+  population, $\tage$, and $\Mbh$.  This is illustrated in
   Figure~\ref{fig:vweff}. For black hole masses below $10^7 \Msun$ SNe
@@
 stellar population, and will realistically vary between $\sim 0.1$ and
-$\sim 1$.
+$\sim 1$ (see Appendix~\ref{app:eta}).
 
-For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that rad
+For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling},
+that radiative cooling is negligible. On the other hand, for
+$\vwO$=200 km/s radiative cooling would be quite important for many of
+our profiles and should be included.
 
@@
 \label{app:rs}
-\input{appendix}
+\input{rs}
 

### 2014-09-02 rs.tex
Fixing typos in manuscript and commiting both appendices.

It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density at $\rs$.  Consider the steady-state entropy equation.

\begin{align}
&\rho T v \dsdr=\Q\\
&\dsdr=\frac{\Q}{\rho T v} \label{eq:ss_entropy}
\end{align}

t $\rs$, the velocity, $v$ goes to zero.  Therefore, the numerator must also go to 0. This implies that the  temperature at the $\rs$ is given by

\begin{align}
 &\frac{\kb T}{\mu \mp}=\gammafi \kew 
\end{align}

From the first law of thermodynamics

\begin{align}
T\dsdr&=\ddr{u}+p\ddr{(1/\rho)}\\
&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho^2}\ddr{\rho}\\
&=\frac{1}{\gamma-1}\ddr{(p/\rho)}-\frac{p}{\rho} \underbrace{\dxdy{\log{\rho}}{\log{r}}}_{-n} \label{eq:first_law}
\end{align}

Combining Equation~\ref{eq:first_law} and Equation~\ref{eq:ss_entropy}, one obtains.

\begin{align}
\frac{1}{\gamma-1}\ddr{(p/\rho)}+r n \cs=\frac{\Q}{\rho  v} \label{eqn:combo1}
\end{align}

At the stagnation point we also have (from the momentum equation)

\begin{align}
&\frac{1}{\rho}\dpdr=-\dphidr\\
&\ddr{(p/\rho)}-r n \cs=-\dphidr \label{eqn:HSE}
\end{align}

Then multiplying Equation~\ref{eqn:HSE}  $\frac{1}{\gamma-1}$ and subtracting it from Equation~\ref{eqn:combo1} we obtain

\begin{align}
\gammaf r n \cs = \frac{1}{\gamma-1} \dphidr + \frac{\Q}{\rho  v}
\end{align}

From the above equation we may obtain an expression for the Stagnation point using L'Hopital's rule and Equation~\ref{eq:tstag}. To obtain an analytic expression, we take $\Mstar\sim r^{2-\Gamma}$

\begin{align}
&\kewO n =A \phirs -B \frac{G \Mbh}{\rs}\\
&A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} 
\end{align}

Note that in the above expression $\Mstar$ is evaluated at the stagnation radius. Let $\omega=\Mstar(\rs)/\Mbh$ and 
$\eta=v_{w,0}/\sigma_{\rm soi}$. We may re-parameterize this relationship as follows:

\begin{align}
\x=\frac{1}{\eta^2 n}\left[ (1+\omega)\left(A-\frac{n}{2}\right)-B\right]
\end{align}

Note that in general $\omega$ is an implicit function of $x$. Cusp galaxies have $\Gamma\simeq1$.  Then $\omega=x$. With $\gamma=5/3$, $A=2$ and $B=1/4$.  Then:

\begin{align}
\x=\frac{7-2n}{2\eta^2 n+2n-8}
\end{align}

Consider the limit $\lim_{\eta \to 0}$ (the extra heating $\vwO$ goes to 0. Then we will get a negative value for the stagnation radius unless the gas density profile is quite steep at the $\rs$: $3.5<n<4$...

In contrast for a core galaxy we will have $\Gamma\simeq0, A=9/4, B=1/2$, and  $\omega=x^2$. Thus we will have a quadratic equation for stagnation radius, which gives

\begin{align}
\x=\frac{\eta^2 n \pm \sqrt{\eta^4 n^2 -4 \left(\frac{9}{4}-\frac{n}{2}\right) \left(\frac{7}{4}-\frac{n}{2}\right)}}{2\left(\frac{9}{4}-\frac{n}{2}\right)}
\end{align}

Consider the limit $\lim_{\eta \to 0}$, then for $\rs$ to exist we must have $3.5<n<4.5$.

When $\Mstar << \Mbh$ at the stagnation radius, the relationship between $\rs$ and $\vw$ is greatly simplified.

\begin{align}
\kewO=\frac{7}{4}\frac{G \Mbh}{n \rs}
\end{align}

Where the pre-factor on the right-hand side is valid for $\gamma=5/3$ and $\Gamma=1$ or 0.

### 2014-09-04 ms.tex
Beginnings of angular momentum section.

@@
 \newcommand{\rb}{r_b}
+\newcommand{\rcirc}{r_{\rm circ}}
+\newcommand{\rss}{r_{\rm ss}}
+\newcommand{\lrs}{\l_{\rs}}
+\newcommand{\lambdars}{\lambda_{\rs}}
 \newcommand{\vw}{v_w}
@@
 \begin{align}
-\dot{M}=\frac{\eta \Menc(\rs)}{\rs}
+\dot{M}=\frac{\eta \Menc(\rs)}{\th}
 \end{align}
@@
 
-\[
+\begin{align}
 \Lambda(T)\simeq
@@
 \label{eq:cooling}
-\]
+\end{align}
 
@@
 The heating rate is estimated as $q \vw^2/2$.
-The ratio is computed assuming $eta=1$.}
+The ratio is computed assuming $\eta=1$.}
 \end{figure}
@@
 \subsection{Angular Momentum}
+\label{sec:ang}
+Our models are spherically symmetric and do not include the effects of
+the gas' angular momentum. However, galaxies will in general have some
+net rotation, and the gas will generally have some non-zero angular
+momentum. At some radius, $\rcirc$, the specific angular momentum of
+the gas will equal the specific angular momentum of a circular
+orbit. Inside of this radius our assumptions of no rotation and
+spherical symmetry will break down. But if $\rcirc$ inner sonic point
+of the flow, the region where angular momentum becomes important will
+be causally disconnected from the rest of the flow, and we would be
+justified in neglecting angular momentum (at least on large scales).
 
+The inner sonic point, $\rss$ general occurs at $\simq 1\%$ of
+$\rinf$. $\rcirc$ depends on the gas injection radius. The largest
+injection radius is $\rs$. Let $\lrs$ be the gas specific angular
+momentum at $\rs$, then
+
+\begin{align}
+\rcirc=\frac{\lrs}{G \Mbh}
+\end{align}
+
+ used two-dimensional kinematic data to measure the ratio of ordered
+ to random motion in a sample of early type galaxies. More precisely,
+ they measure
+
+\begin{align}
+\lambda_R=\frac{\left<R|V|\right>}{\lef<R\sqrt{V^2+\sigma^2}\right>}
+\end{align}
+
+Where $R$ is the distance is the distance from the galactic center, $V$ is
+the mean stellar velocity, and $\sigma$ is the velocity
+disperison. The brackets represent a luminosity weighted average.
+
+$\lrs\simeq\lambdars \sigma(\rs)^2 \rs^2$ 
 \section{Summary}

### 2014-09-11 ms.tex
Ang momentum section and other improvements in language

@@
 \usepackage{astro}
-%\usepackage{natbib}
+% \usepackage{natbib}
+
+% \renewcommand{\l}{\left}
+% \renewcommand{\r}{\right}
 
@@
 \newcommand{\Mbheight}{M_{\bullet,8}}
-\newcommand{\MbhNorm}{\frac{\Mbh}{10^8 \Msun}}
+\newcommand{\MbheightExp}{\frac{\Mbh}{10^8 \Msun}}
 
@@
 
-%%Maybe active galaxies constitute 10% need reference here?
+%% Maybe active galaxies constitute 10% need reference here?
 Supermassive black holes (SMBHs) are present in the centers of most,
@@
 rate also has implications for rate of black hole growth.
-%AG:Perhaps need more detail here.
+% AG:Perhaps need more detail here.
 
@@
 occupation fraction could be underestimated at low $\Mbh$.
-%AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
+% AG: In our model we obtain a steeper relationship, but we have difficulty matching the observed relationship above the detection threshold
 
@@
 the SMBH, should cause a cusp in the gas temperature profile (assuming
-the kinetic energy of stellar winds is efficiently themalized in
+the kinetic energy of stellar winds is efficiently thermalized in
 shocks).
-%%AG-give sense of scale.
+%% AG-give sense of scale.
 
@@
 stellar winds and supernova heating.
- %%AG--say something about x-ray observations.
+%% AG--say something about x-ray observations.
 
@@
 galaxies, while $\gamma\simeq0$ for core galaxies.
-%AG:Is there a systematic dependence of beta on galaxy type$.
+% AG:Is there a systematic dependence of beta on galaxy type$.
 
@@
 sample.  Gas is supplied by winds from the stellar population in the
-galactic center. Assuming a rate of mass injection, $q$, spherical
-symmetry and an ideal gas equation of state.
+galactic center. The equation we solve are
 
@@
   &\rho \frac{dv}{dt}=-\dpdr-\rho \dphidr-q v\\
-&\rho T \frac{ds}{dt}=q\left[\ke+\kew+\gammaf \cs \right]
+  &\rho T \frac{ds}{dt}=q\left[\ke+\kew+\gammaf \cs \right].
 \end{align}
+
+Note that we assume spherical symmetry, an ideal gas equation of
+state, and rate of mass injection $q$. $q$ is related to related to
+the stellar density $\rhostar$ via
+
+\begin{align}
+  q=\frac{\eta \rho_*}{\th}.
+\end{align}
+
+%% AG $eta/th$ is the specific of rate of mass return to the ISM.  Ciotti et al. 1991 -- see in particular Table 2. 
+Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this number will lie in the range $\sim$0.1-1 (see Appendix~\ref{app:eta}).
+We adopt $\eta=1$.
+However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.
+
+$\vw^2/2$ encapsulates heating in our simulation.
+We take $\vw^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.
 
@@
 
-$q$ represent the rate of injection of gas mass per unit volume, and
-is derived from the stellar density, $\rho_*$, using
-
-\begin{align}
-q=\frac{\eta \rho_*}{t_h}
-\end{align}
-
-%%AG $eta/th$ is the specific of rate of mass return to the ISM.  Ciotti et al. 1991 -- see in particular Table 2. 
-Where $t_h$ is the Hubble time, and $\eta$ is an efficiency parameter--for a stellar population between 2-15 Gyr old, this number will lie in the range $\sim$0.1-1 (see Appendix~\ref{app:eta}).
-We adopt $\eta=1$.
-However, scaling $\eta$ by some factor, would simply scale the $\rho$ by the same factor and otherwise leave the solution unchanged.
-
-$\vw^2/2$ encapsulates heating in our simulation.
-We take $\vw^2=\sqrt{\sigma(r)^2+v_{w,0}^2}$ where $\sigma(r)$ corresponds to the velocity dispersion of the stars and $v_{w,0}$ accounts for additional heating sources (ms pulsars, SNe Ia, etc.)  We approximate $\sigma(r)$ to be given by $G \Menc/r=G(\Mbh+\Mstar)/r$, where $\Mbh$ is the mass of the SMBH and $\Mstar$ is the stellar mass inside radius $r$.
-
-% {\bf NCS: here is some added detail about the role of stellar mass
-% functions in the model}
-
-% if we consider different star formation scenarios (for example,
-% continuous star formation) or different IMFs, it will change.  Once
-% these free parameters are specified, however, we can answer an
-% important question: do young stellar populations increase or
-% decrease the SMBH feeding rate $\dot{M}$?  Clearly, $\eta(t)$ is
-% larger for young stellar populations, but these stars also have high
-% wind velocities that diminish the stagnation radius.  Crudely
-% approximating $v_{\rm w}=200~{\rm km~s}$ for $m_{\rm max} <
-% 10M_{\odot}$ and $v_{\rm w}=1000~{\rm km~s}$ for $m_{\rm max} >
-% 10M_{\odot}$ (motivated by the transition from dust-driven wind loss
-% on the AGB to line-driven wind loss on the main sequence), we can
-% employ the relation $\dot{M} \propto \eta(t) r_{\rm
-% s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_*
-% \propto r^{-\Gamma}$) to determine the impact of stellar ``youth''
-% on SMBH feeding rates.
-%
-%\begin{figure}
-%\includegraphics[width=\columnwidth]{NickPlot.eps}
-%\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.
-The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.
-Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation.}
-%\end{figure}
-%
-%%In Fig.
-\ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a function of time, for three different stellar density profiles $\Gamma = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an influence radius $r_{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$ SMBH).
-We parametrize the wind velocity as
-%\begin{equation}
-%\frac{v_{\rm w}}{\rm km~s^{-1}}=600-400\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm yr}}\right).
-%\end{equation}
-%The ``impulsive burst'' mode of star formation produces large ($\sim 10$) differences between the three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is large.
-We also plot, as dotted curves, a simple model for the ``continuous'' mode of star formation, where mass loss is calculated as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average energy injection in the wind is calculated as $\bar{v_{\rm w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm km~s}^{-1})^2$.
-Interestingly, the continuous mode of star formation produces small differences from late-time $\dot{M}$ seen in cusp galaxies with impulsive star formation; however, continuous mode star formation decreases late-time $\dot{M}$ by an order of magnitude relative to impulsive star formation in core galaxies.
-
 \section{Solutions}
 \subsection{Analytics: Flow properties at $\rs$}
-It is possible to derive an analytic expression for the steady-state stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of the density (at $\rs$) $n$.
-We summarize the main results here and place the detailed derivation in Appendix~\ref{app:rs}.
+It is possible to derive an analytic expression for the steady-state
+stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of
+the density (at $\rs$) $n$.  We parameterize our results in terms of
+$\vwOFH=\vwOFHexp$, $\Mbheight=\MbheightExp$ and
+$\xi=\left(1+\frac{0.14 \Mbheight^{0.43}}{\vwOFH}\right)^{1/2}$ . $xi$
+encapsulates the contribution of $\sigma$ in the heating.  We
+summarize the main results here and place the detailed derivation in
+Appendix~\ref{app:rs}.
 
@@
   &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}\\
- &T=6 \times 10^6 {\rm K} \, \mu \, \left({\frac{\vw}{500 \,{\rm km/s}}}\right)^2 
+  &T=6 \times 10^6 {\rm K} \,  \,\ \vwO500^2 \xi^2 \mu
 \end{align}
 
+%%Need this to be consistent with our new vw convention.
 We may also write an (implicit) analytic expression for $\rs$
@@
   &\rs=\frac{7}{2}\frac{G \Mbh}{n \vw^2}\\
-&\simeq 6 \, \pc \left(\MbhNorm\right) \left(\vwOFH\right)^{-2}
+  &\simeq 6 \, \pc \,\, \Mbheight \left(\vwOFH\right)^{-2}
   \label{eq:stag_simple}
@@
   \begin{cases}
-   1.5 \times 10^{-3}  \left(\Mbheight\right)^{1.9}
-   \left(\vwOFH\right)^{-4} \eta \Msun \, \pyear& \text{for core galaxies} \\
-   3.3 \times 10^{-3} \left(\Mbheight\right)^{1.4}
-   \left(\vwOFH\right)^{-2} \eta \Msun \, \pyear  & \text{for cusp
-     galaxies} 
+    1.6 \times 10^{-3}  \left(\Mbheight\right)^{1.9}
+    \left(\vwOFH\right)^{-4} \xi^{-4} \eta \Msun \, \pyear& \text{for cores} \\
+    3.4 \times 10^{-3} \left(\Mbheight\right)^{1.4}
+    \left(\vwOFH\right)^{-2} \xi^{-2} \eta \Msun \, \pyear  & \text{for cusps} 
   \end{cases}
@@
   \begin{cases}
-2.5 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \eta \, {\rm g \, cm^{-3}}& \text{for   galaxies}\\
-5.5 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH    \eta \, {\rm g \,cm^{-3}} & \text{for cursp galaxies}
+    2.6 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \xi^{-1} \eta \, {\rm g \, cm^{-3}}& \text{for cores}\\
+    5.6 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH  \xi^{-1}  \eta \, {\rm g \,cm^{-3}} & \text{for cusps}
   \end{cases}
@@
 
-%%AG: Describe conservation checks to additionally validate the results.
+%% AG: Describe conservation checks to additionally validate the results.
 
@@
   Also, MSPs may also be dissociated in the galactic center...
-%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
+  %% Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
 
@@
 
-Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs
-and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which
-gives $\vwO\simeq 230 \, \eta^{-1/2}$ km/s (For $\eta=0.1$ this
-corresponds to $\vwO\simeq$ 500 km/s.
- %Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.
+  % Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs
+  % and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which
+  % gives $\vwO\simeq 230 \, \eta^{-1/2}$ km/s (For $\eta=0.1$ this
+  % corresponds to $\vwO\simeq$ 500 km/s.
+  % Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.
 
   As noted in \citealt{ShcherbakovWong+:2014a}, SNe energy injection
- cannot necessarily be treated as constant throughout time and space,
- since the flow time-scale may be short compared to the time between
- successive SNe Ia.
+  cannot necessarily be treated as constant throughout time and
+  space. This would only make sense if many SNes are exploding on the
+  dynamical timescale of the flow.
 
-There will be some radius, $\rIa$, where the dynamical timescale of
-the flow becomes comparable to the time between successive Type Ia
-SNe.  If the stagnation radius ($\rs$) of the flow is outside of
-$\rIa$ then SNes will provide a steady contribution to $\vwO$
+  To check this quantitatively we may compare the radius where the
+  dynamical timescale becomes comparable to the time between successive
+  Ias, $\rIa$, to the stagnation radius, $\rs$. If $\rIa>>\rs$, SNes
+  will provide a steady contribution to the $\vwO$.
 
@@
   % illustrated in Figure~\ref{fig:vw_eff}.
-%\end{enumerate}
+  % \end{enumerate}
 
@@
 heating rate.
-%%AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
-%%AG-Note separation of cores and cusps (at vw=1000 km/s, where there are enough core galaxies for this comparison to be made). Also, note that the spread in core galaxies is far larger.
+%% AG-The variation in accretion rate for w/ vw for core galaxies is comparable to that of cusp galaxies and belies the steep dependence stated above.
+%% AG-Note separation of cores and cusps (at vw=1000 km/s, where there are enough core galaxies for this comparison to be made). Also, note that the spread in core galaxies is far larger.
 
@@
 
-%%AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).
+%% AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).
 
 \subsection{Comparison with observations}
+\subsubsection{Comparison with observed gas temperatures and densities}
 \citealt{AllenDunn+:2006a} use Chandra x-ray observations to infer the
 temperature and density profiles for nine nearby x-ray luminous
-elliptical galaxies.  Five of the galaxies in their sample overlap
-with that in \citetalias{WangMerritt:2004a}.
+elliptical galaxies.  \citealt{RussellMcNamara+:2013a} performed a
+similar analysis with a somewhat enlarged sample.
+% At some point it would be useful to describe the differences between
+% these two sets of observations \citealt{RussellMcNamara+:2013a}
+% tries several different extrapolation schemes for the gas density,
+% and finds that that the uncertainty in extrapolating the density
+% profile is the dominant source of uncertainty in measuring the
+% accretion rate. Find total number which overlaps once the Russell
+% galaxies are included...
+Five of the galaxies in their sample overlap with that in \citetalias{WangMerritt:2004a}.
 
@@
 inferred from observations for the overlapping galaxies.  Note that we
-we have two free parameters ($\eta$ and $\vwO$ in our model and thus
-we can can always match $T$ and $\rho$ at least one point.  We
-generally find that $\vwO=500$ km/s (as would be expected from SNe Ia)
-gives rough agreement with the observed temperatures.  Thus, we choose
-$\vwO=500$ km/s.  We choose an $\eta$ so that our solution would be
-consistent with the observed density profiles. The comparison is shown
-in Figure~\ref{fig:allen_compare}.
-%%AG-The chosen properties, in particular eta may be summarized in a table.
+we have two free parameters ($\eta$ and $\vwO$) in our
+model. Therefore, we can always match the observed $T$ and $\rho$
+profiles for at least one point.  We generally find that $\vwO=500$
+km/s (as would be expected from SNe Ia) gives rough agreement with the
+observed temperatures. 
+% Thus, we choose $\vwO=500$ km/s.  We choose an
+% $\eta$ so that our solution would be consistent with the observed
+% density profiles. The comparison is shown in
+Figure~\ref{fig:allen_compare}.
+%% AG-The chosen properties, in particular eta may be summarized in a table.
+%% AG-Mention rising temperature profiles on large scales.
 
 \begin{itemize}
-\item \emph{NGC4486} %eta=0.2
-  On scales of $\sim1$ kpc the density profile in
-  \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
-  has a break in the gas density at $\sim 300$ pc--near the location
-  of the Nuker break radius for this galaxy at 560 pc. There is an
-  observed break in the density, but on a scale of a few kpc.
+% \item \emph{NGC4486} %eta=0.2
+%   On scales of $\sim1$ kpc the density profile in
+%   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
+%   has a break in the gas density at $\sim 300$ pc--near the location
+%   of the Nuker break radius for this galaxy at 560 pc. There is an
+%   observed break in the density, but on a scale of a few kpc.
 
-  In contrast to a naive extrapolation of the observed $T$ and $\rho$
-  to smaller scales, our models have $T$ and $\rho$ monotonically
-  increasing towards the galactic center. The increase in $T$ is due
-  to the increased velocity dispersion (and thus increased heating)
-  towards the galactic center.
+%   The temperature is assumed to be flat from the resolution limit
+%   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
+%   increases monotonically towards the galactic center. This increase
+%   is due to the increased velocity dispersion (and thus increased
+%   heating) towards the galactic center.
+
+\item \emph{NGC5813} %eta=0.1
+  The observed density profile \citealt{RussellMcNamara+:2013a} is
+  shallower than our calculated density profile, which has a sharp
+  break at $\sim$0.1 kpc, the location of the break radius in the
+  Nuker profile (this is the radius where the stellar light profile
+  transitions from a shallower inner power law slope to a steeper
+  outer power law slope.
+
+  For this galaxy we found that we could reproduce the observed
+  temperature on large scales with $\vwO=500$ km/s. The increased
+  velocity disperision towards the galactic center results in a sharp
+  increase in $T$ at small radii, which is not captured in the
+  observations due to resolution issues.
 \end{itemize}
 
+%It would be nice to have error bars for the observational points in this plot...
 \begin{figure*}
-\includegraphics[width=\columnwidth]{T_compare.eps}
-\includegraphics[width=\columnwidth]{dens_compare.eps}
-\caption{\label{fig:allen_compare} Comparison of $n_e$ and $T$ to the \citealt{AllenDunn+:2006a}}. 
-%%AG in the future we will have to be carfeful of the mean molecular weight.
+  \includegraphics[width=\columnwidth]{NGC5813_T.eps}
+  \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
+  \caption{\label{fig:allen_compare} Comparison of $n_e$ and $T$ to
+    the profiles in \citealt{AllenDunn+:2006a} and \citealt{ RussellMcNamara+:2013a}}.
+  %% AG in the future we will have to be carfeful of the mean molecular weight.
 \end{figure*}
@@
 
-For each of our solutions we compare the radiative cooling rate, $C$
-to the heating rate $H=q \vw^2/2$. If $H/C \gg 1$ then cooling may be
-neglected. We take
+To assess the importance of radiative cooling for our solutions we
+compare the radiative cooling rate, $C$ to the heating rate $H=q
+\vw^2/2$. If $H/C \gg 1$ then cooling may be neglected. We take
 
@@
 
+%% at low densities there might be some sort of non-CIE cooling operating.
 Where $n$ is the number density and $\Lambda(T)$ is the cooling
@@
 for solar metallicity--see Figure 34.1 in \cite{Draine:2011a})
-%cite Draine
 
@@
   orbit. Inside of this radius our assumptions of no rotation and
-spherical symmetry will break down. But if $\rcirc$ inner sonic point
-of the flow, the region where angular momentum becomes important will
-be causally disconnected from the rest of the flow, and we would be
-justified in neglecting angular momentum (at least on large scales).
+  spherical symmetry will break down. But if $\rcirc$ is inside of the
+  inner sonic point of the flow, the region where angular momentum
+  becomes important will be causally disconnected from the rest of the
+  flow, and we would be justified in neglecting angular momentum (at
+  least on large scales).
 
-The inner sonic point, $\rss$ general occurs at $\simq 1\%$ of
-$\rinf$. $\rcirc$ depends on the gas injection radius. The largest
+  $\rcirc$ depends on the gas injection radius. The largest
   injection radius is $\rs$. Let $\lrs$ be the gas specific angular
@@
 
- used two-dimensional kinematic data to measure the ratio of ordered
- to random motion in a sample of early type galaxies. More precisely,
- they measure
+  \citealt{EmsellemCappellari+:2007a} used two-dimensional kinematic
+  data to measure the ratio of ordered to random motion in a sample of
+  early type galaxies. More precisely, they measure
 
   \begin{align}
-\lambda_R=\frac{\left<R|V|\right>}{\lef<R\sqrt{V^2+\sigma^2}\right>}
+    \lambda_R=\frac{\left<R|V|\right>}{\left<R\sqrt{V^2+\sigma^2}\right>}
   \end{align}
@@
   the mean stellar velocity, and $\sigma$ is the velocity
-disperison. The brackets represent a luminosity weighted average.
+  dispersion. The brackets represent a luminosity weighted average.
 
-$\lrs\simeq\lambdars \sigma(\rs)^2 \rs^2$ 
+  We may rewrite the specific angular momentum at $\rs$ in terms of $\lambda_R$.
+
+  \begin{align}
+    \lrs\simeq\lambdars \sigma(\rs)^2 \rs^2
+  \end{align}
+
+  Then
+
+  \begin{align}
+    \rcirc&\simeq\lambdars^2 \frac{\sigma(\rs)^2}{G \Mbh} \rs^2\\
+    &\simeq\lambdars^2 \frac{\rs^2}{\rsoi} \lsim \lambdars^2 \rsoi
+  \end{align}
+
+  The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
+  $\rsoi$. %%AG-Need to explain this somehow.
+  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Figure 2 of
+  \citealt{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
+  of radius for a sample of early type galaxies. On scales of $\sim 0.1
+  R_e$ $\lambda_R$ is either less than 0.1 or rapidly declining for most
+  of their sample %%need to be clearer on rapidly declining also compare
+  %% this scale to the sphere of influence scale.
+  This suggests that angular momentum should generally be unimportant.
+
   \section{Summary}
 
+  \clearpage
   \appendix
-\clearpage
   \section{Analytic Expression for the stagnation radius}

### 2014-09-15 ms.tex
Updating one of the figures. And expanding captions.

@@
 \newcommand{\rIa}{r_{\rm Ia}}
+\newcommand{\EIa}{E_{\rm Ia}}
+\newcommand{\RateIa}{R_{\rm Ia}}
 \newcommand{\sigsoi}{\sigma_{\soi}}
@@
 $\vwOFH=\vwOFHexp$, $\Mbheight=\MbheightExp$ and
-$\xi=\left(1+\frac{0.14 \Mbheight^{0.43}}{\vwOFH}\right)^{1/2}$ . $xi$
+$\xi=\left(1+\frac{0.14 \Mbheight^{0.43}}{\vwOFH}\right)^{1/2}$. $\xi$
 encapsulates the contribution of $\sigma$ in the heating.  We
@@
   &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}\\
-  &T=6 \times 10^6 {\rm K} \,  \,\ \vwO500^2 \xi^2 \mu
+  &T=6 \times 10^6 {\rm K} \,  \,\ \vwOFH^2 \, \xi^2 \mu
 \end{align}
@@
 \begin{align}
-  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vw^2}\\
+  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2}\\
   &\simeq 6 \, \pc \,\, \Mbheight \left(\vwOFH\right)^{-2}
@@
   \begin{cases}
-    2.6 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \xi^{-1} \eta \, {\rm g \, cm^{-3}}& \text{for cores}\\
-    5.6 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH  \xi^{-1}  \eta \, {\rm g \,cm^{-3}} & \text{for cusps}
+    2.6 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \xi^{-1} \eta \,
+    \, {\rm g \, cm^{-3}}& \text{for cores}\\
+    5.6 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH  \xi  \eta \,\, {\rm g \,cm^{-3}} & \text{for cusps}
   \end{cases}
@@
   \includegraphics[width=\columnwidth]{rs.eps}
-  \caption{\label{fig:stag}$\x$ vs. $\vwNorm$}
+  \caption{\label{fig:stag} \emph{Top panel:} $\x$ vs. $\vwNorm$ for
+    our sample for three different values of $\vwO$. Blue is
+    $\vwO=1000$ km/s, orange is $\vwO=500$ km/s and green is
+    $\vwO=200$ km/s. Squares correspond to cusp galaxies, while
+    triangles correspond to cores. \emph{Bottom panel}: Fractional difference
+    between numerical $x$ and the analytic result in
+    Equation~\ref{eq:stag_analytic}. Points are colored in the same
+    way as in the top panel.}
 \end{figure}
@@
 \item \emph{Type Ia SNe} From he energy injected per Ia SNe,
-  $E_{\rm Ia}$, and the SNe rate, $R_{\rm Ia}$
+  $E_{\rm Ia}$, and the SNe rate (per stellar mass), $R_{\rm Ia}$
 
@@
     \vwO=\sqrt{\frac{2 t_h R_{\rm Ia} E_{\rm Ia}}{\eta}} \label{eq:vw_sne}
+  \end{align}
+
+  $\EIa \simeq10^{51}$ ergs. $\RateIa$ will depend on the age of the
+  stellar population. $\eta$ can be calculated using
+  Equation~\ref{eq:eta} in Appendix~\ref{app:eta}. $\RateIa$ may be
+  calculated using the delay time distribution in
+  \citealt{MaozMannucci+:2012a}. Generally, $\RateIa$ is the
+  convolution of the star formation rate and the delay time
+  distribution divided by the present stellar mass. In the limit of
+  impulsive star formation, $\RateIa$ is the delay time distribution
+  evaluated at the time since the star formation episode. The delay
+  time distribution plotted in Figure 1 of
+  \citealt{MaozMannucci+:2012a}, and has a functional form
+
+  \begin{align}
+    \Psi(\tau)=\frac{.03
+      \left(\tau/10^8\right)^{-1.12}}{10^{10} \Msun}
   \end{align}
@@
 
+  %AG--this would need to be adjusted to account for the delay time
+  %distribution...
   \begin{align}
@@
     \includegraphics[width=\columnwidth]{vw-contour.eps}
-    \caption{\label{fig:vweff} Overall $\vwO$ for $\Mbh$-Stellar Age parameter space.}
+    \caption{\label{fig:vweff} Overall $\vwO$ for $\Mbh$-Stellar Age
+      parameter space. The contribution from stellar winds is taken to
+      be $100$ km/s. The contribution from SNe Ia is calculated using
+      Equation~\ref{eq:vw_sne}. The contribution from SNe Ia is only
+      added if the $r_s$ corresponding to the resulting $\vwO$ is
+      outside $\rIa$.}%describe other cases here.
   \end{figure}
@@
   \includegraphics[width=\columnwidth]{mdot_mass.eps}
-  \caption{\label{fig:mdot_mass}$\eddr$ vs. $\Mbh$}
+  \caption{\label{fig:mdot_mass}$\eddr$ vs. $\Mbh$ for our sample. for
+    our sample for three different values of $\vwO$. Blue is
+    $\vwO=1000$ km/s, orange is $\vwO=500$ km/s and green is
+    $\vwO=200$ km/s. Squares correspond to cusp galaxies, while
+    triangles correspond to cores.}
 \end{figure}
@@
   transitions from a shallower inner power law slope to a steeper
-  outer power law slope.
+  outer power law slope).
 

### 2014-09-15 ms.tex
Some changes in wording and small modification for figures

@@
 quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq
-0.7-0.8$ \citep{MillerGallo+:2014a}. If $L_X\sim\dot{M}^2$, this would
-suggest $\eddr\sim \Mbh^{-0.6}$. In contrast for fixed $\vwO$ and
-$\eta$ we obtain that $\eddr\sim \Mbh^{0.5-1}$. One possible solution
-is that $\eta$ decreases with $\Mbh$. $\dot{M}$ scales linearly with
-$\eta$, so we would need to have $\eta\sim \Mbh^{-1}$ to explain the
+0.7-0.8$ \citep{MillerGallo+:2014a}. In our model we have $\Mdot \sim
+\Mbh^{1.5-2}$. If $L_x\sim M$, then we would have $\L_x \sim
+\Mbh^{1.5-2}$, steeper than the observed relationship. (If $L_x \sim
+\Mdot^2$ the discrepance becomes worse).  One possible solution • is
+that $\eta$ decreases with $\Mbh$.  $\Mdot$ scales linearly with
+$\eta$, so we would need to have $\eta \sim \Mbh^{-1}$ to explain the
 observed downsizing trend.

### 2014-09-16 ms.tex
Update ms.tex

@@
 fraction.  For example, \citealt{MillerGallo+:2014a} used an observed
-relation between $\Mbh$ and nuclear x-ray luminosity $L_x$ to
+relation between $\Mbh$ and nuclear X-ray luminosity $L_x$ to
 constrain the BH occupation fraction.  However, they extrapolate
